### 2014-07-02 uTAS2014/paper.tex
started the manuscript

\documentclass{article}
usepackage[utf8]{inputenc}

\title{3D Printed Microfluidic Devices for Oxygen Control in Cell Culture}

\usepackage{natbib}
\usepackage{graphicx}

\usepackage{fontspec}
\setmainfont{Times New Roman}

\begin{document}

\maketitle

\section{INTRODUCTIOM}

This is a reference \cite{Au2014}.

\section{EXPERIMENTAL}

\section{RESULTS AND DISCUSSION}

\begin{figure}[h!]
\centering
\includegraphics[scale=1.7]{3-inch-well-photo.png}
\caption{3" petri dish device}
\label{fig:3-inch-well-photo}
\end{figure}

\section{CONCLUSION}

\bibliographystyle{plain}
\bibliography{references}
\end{document}

### 2014-07-21 uTAS2014/paper.tex
worked on paper.tex and update .gitignore for latex
added content from abstract, fixed citations

@@
 \documentclass{article}
-usepackage[utf8]{inputenc}
+\usepackage[utf8]{inputenc}
 
@@
 
-\usepackage{fontspec}
-\setmainfont{Times New Roman}
+%\usepackage{fontspec}
+%\setmainfont{Times New Roman}
 
@@
 
-\section{INTRODUCTIOM}
+\section{INTRODUCTION}
 
-This is a reference \cite{Au2014}.
+3D printing of microfluidic devices enables rapid, one-step fabrication of complex designs infeasible to make with planar lithography and replica molding techniques.
+In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
+On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which is outsourced to a 3D printing company for around \$100/device \cite{Au2014, Chen2014}.
+Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
+3D CAD models are designed and printed with microfluidic delivery channels, and then completed by adhering a gas permeable membrane of PDMS (Polydimethylsiloxane) to enable diffusion of gas to the culture area.
+Two devices are presented and characterized: one is a large area (3” diameter) open-well format, and the second is an insert for a standard 24 well plate as shown in Figure 1.
 
 \section{EXPERIMENTAL}
+
+The 3” petri dish device contains a 500 μm wide channel following a serpentine path leaving 500 um of spacing between channels and has integrated hose barbs directly printed onto the device.
+The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work and also incorporates integrated hose barbs \cite{Oppegard2010}.
+This is a prototype intended to be expanded to control all 24 wells.
+A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells.
+The device also features a ‘pipe within a pipe’ design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing.
+A PDMS membrane is adhered to the microchannels of both designs by spin coating a thin PDMS membrane and using PDMS as an adhesive.
+Both devices were printed by Fineline Prototyping in Watershed XC using stereolithography.
+Oxygen was measured in the 3” petri dish device with a commercial fiber-optic probe and the 24 well insert was quantified with a planar oxygen sensor as shown in Figure 2.
 
@@
 
+3D printing allows complex designs, integrated tubing connectors, and is comparable in price to standard PDMS fabrication.
+This technique represents a bridge to commercialization where robust devices can be more easily shared and disseminated.
+While injection molding, hot embossing, or other industrial processes are cheaper when making hundreds to thousands of devices, it is not practical to make a injection mold when making tens to hundreds of devices.
+In addition, PDMS fabrication would be too time consuming, expensive, and the failure rate would be unacceptable.
+3D printing is a perfect solution to these device fabrication needs.
+
 \bibliographystyle{plain}

### 2014-07-21 uTAS2014/paper.tex
made one line, fixed figure size

@@
 In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
-On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which is outsourced to a 3D printing company for around \$100/device \cite{Au2014, Chen2014}.
+On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which is outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
 Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
@@
 
-The 3” petri dish device contains a 500 μm wide channel following a serpentine path leaving 500 um of spacing between channels and has integrated hose barbs directly printed onto the device.
+The 3” petri dish device contains a 500 $\mu$m wide channel following a serpentine path leaving 500 $\mu$m of spacing between channels and has integrated hose barbs directly printed onto the device.
 The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work and also incorporates integrated hose barbs \cite{Oppegard2010}.
@@
 \centering
-\includegraphics[scale=1.7]{3-inch-well-photo.png}
+\includegraphics[scale=0.2]{3-inch-well-photo.png}
 \caption{3" petri dish device}

### 2014-07-22 uTAS2014/paper.tex
added figure and made figure references

@@
 3D CAD models are designed and printed with microfluidic delivery channels, and then completed by adhering a gas permeable membrane of PDMS (Polydimethylsiloxane) to enable diffusion of gas to the culture area.
-Two devices are presented and characterized: one is a large area (3” diameter) open-well format, and the second is an insert for a standard 24 well plate as shown in Figure 1.
+Two devices are presented and characterized: one is a large area (3” diameter) open-well format, and the second is an insert for a standard 24 well plate as shown in Figure \ref{fig:6-well-photo}.
 
@@
 Both devices were printed by Fineline Prototyping in Watershed XC using stereolithography.
-Oxygen was measured in the 3” petri dish device with a commercial fiber-optic probe and the 24 well insert was quantified with a planar oxygen sensor as shown in Figure 2.
+Oxygen was measured in the 3” petri dish device with a commercial fiber-optic probe and the 24 well insert was quantified with a planar oxygen sensor as shown in Figure \ref{fig:6-well-photo}.
 
@@
 \label{fig:3-inch-well-photo}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=0.2]{6-well.JPG}
+\caption{6 well device oxygen control device}
+\label{fig:6-well-photo}
 \end{figure}

### 2014-07-24 uTAS2014/paper.tex
added publication outline

@@
 On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which is outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
+Recently 3D printing has emerged as a method for directly printing complete microfluidic devices (folch, spence, that other one). 
+Printing is currently limited in choice of materials when compared to MEMS style fabrication. 
+As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials.
 Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
-3D CAD models are designed and printed with microfluidic delivery channels, and then completed by adhering a gas permeable membrane of PDMS (Polydimethylsiloxane) to enable diffusion of gas to the culture area.
-Two devices are presented and characterized: one is a large area (3” diameter) open-well format, and the second is an insert for a standard 24 well plate as shown in Figure \ref{fig:6-well-photo}.
 
@@
 The 3” petri dish device contains a 500 $\mu$m wide channel following a serpentine path leaving 500 $\mu$m of spacing between channels and has integrated hose barbs directly printed onto the device.
-The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work and also incorporates integrated hose barbs \cite{Oppegard2010}.
+The 3D part is printed with the channels embedded in the bottom of the petri dish. 
+A 120 μm thick PDMS membrane is adhered across the channels.
+This device allows cell cluture in a large open well format compatible with assays requireing cell scaping.
+The membrane is eaisly peeled away allowing additional fixing/staining assays to be preformed and can also be repaced with a new membrane to reuse the device.
+
+The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{Oppegard2010} and also incorporates integrated hose barbs.
+The pillars extend into each well leaving a $/sim$500 $\mu$m gap for media between the diffusion membrane and the culutre surface at the bottom of the well.
+Diffusion occurs rapidly across this gap allowing control of the dissolved gas environment around the cells. 
 This is a prototype intended to be expanded to control all 24 wells.
 A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells.
-The device also features a ‘pipe within a pipe’ design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing.
-A PDMS membrane is adhered to the microchannels of both designs by spin coating a thin PDMS membrane and using PDMS as an adhesive.
+The device also features a ‘pipe within a pipe’ design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Figure \ref{fgr:well-render}.
+A PDMS membrane is adhered to the microchannels of both designs by spin coating a thin PDMS layer as an adhesive.
+
 Both devices were printed by Fineline Prototyping in Watershed XC using stereolithography.
 Oxygen was measured in the 3” petri dish device with a commercial fiber-optic probe and the 24 well insert was quantified with a planar oxygen sensor as shown in Figure \ref{fig:6-well-photo}.
+3D CAD models are designed and printed with microfluidic delivery channels, and then completed by adhering a gas permeable membrane of PDMS (Polydimethylsiloxane) to enable diffusion of gas to the culture area.
 
 \section{RESULTS AND DISCUSSION}
+
+Two devices are presented and characterized: one is a large area (3” diameter) open-well format, and the second is an insert for a standard 24 well plate as shown in Figure \ref{fig:6-well-photo}.
 
@@
 
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=0.2]{6well-render.png}
+\caption{6 well device oxygen control device}
+\label{fig:6well-render}
+\end{figure}
+
 \section{CONCLUSION}

### 2015-01-14 publishing/plos_template.tex
copied microtas manuscript draft to plosOne paper

% Template for PLoS
% Version 2.0 July 2014
%
% To compile to pdf, run:
% latex plos.template
% bibtex plos.template
% latex plos.template
% latex plos.template
% dvipdf plos.template
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% Be advised that this is merely a template 
% designed to facilitate accurate translation of manuscript content 
% into our production files. 
%
% This template contains extensive comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template 
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication and enters production, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
% the final text of your manuscript.
%
% DO NOT ADD EXTRA PACKAGES TO THIS TEMPLATE unless absolutely necessary.
% Packages included in this template are intentionally
% limited and basic in order to reduce the possibility
% of issues during our production process.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - tabs/spacing/line breaks within cells to alter layout
% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
% - colors, shading, or graphic objects
% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
%
% For sideways tables, use the {rotating} package and use \begin{sidewaystable} instead of \begin{table} in the appropriate section. PLOS guidelines do not accomodate sideways figures.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
%
% Please be sure to include all portions of an equation in the math environment, and for any superscripts or subscripts also include the base number/text. For example, use $mathrm{mm}^2$ instead of mm$^2$ (do not use \textsuperscript command).
%
% DO NOT USE the \rm command to render mathmode characters in roman font, instead use $\mathrm{}$
% For bolding characters in mathmode, please use $\mathbf{}$ 
%
% Please add line breaks to long equations when possible in order to fit our 2-column layout. 
%
% For inline equations, please do not include punctuation within the math environment unless this is part of the equation.
%
% For spaces within the math environment please use the \; or \: commands, even within \text{} (do not use smaller spacing as this does not convert well).
%
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt]{article}

% amsmath package, useful for mathematical formulas
\usepackage{amsmath}
% amssymb package, useful for mathematical symbols
\usepackage{amssymb}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

\usepackage{hyperref}

% line numbers
\usepackage{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% rotating package for sideways tables
%\usepackage{rotating}

% If you wish to include algorithms, please use one of the packages below. Also, please see the algorithm section of our LaTeX guidelines (http://www.plosone.org/static/latexGuidelines) for important information about required formatting.
%\usepackage{algorithmic}
%\usepackage{algorithmicx}

% Use doublespacing - comment out for single spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\topmargin 0.0cm
\oddsidemargin 0.5cm
\evensidemargin 0.5cm
\textwidth 16cm 
\textheight 21cm

% Bold the 'Figure #' in the caption and separate it with a period
% Captions will be left justified
\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2009}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

\pagestyle{myheadings}

%% Include all macros below. Please limit the use of macros.

%% END MACROS SECTION

\begin{document}

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{Title}
}
% Insert Author names, affiliations and corresponding author email.
\\
Author1$^{1}$, 
Author2$^{2}$, 
Author3$^{3,\ast}$
\\
\bf{1} Author1 Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{2} Author2 Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{3} Author3 Dept/Program/Center, Institution Name, City, State, Country
\\
$\ast$ E-mail: Corresponding author@institute.edu
\end{flushleft}

% Please keep the abstract between 250 and 300 words
\section*{Abstract}

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author Summary}

\section*{Introduction}

3D printing of microfluidic devices enables rapid, one-step fabrication of complex designs infeasible to make with planar lithography and replica molding techniques.
In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which is outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
Recently 3D printing has emerged as a method for directly printing complete microfluidic devices (folch, spence, that other one). 
Printing is currently limited in choice of materials when compared to MEMS style fabrication. 
As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials.
Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.

This is a test of the citations \cite{oppegard2010}.

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}

The 3” petri dish device contains a 500 $\mu$m wide channel following a serpentine path leaving 500 $\mu$m of spacing between channels and has integrated hose barbs directly printed onto the device.
The 3D part is printed with the channels embedded in the bottom of the petri dish. 
A 120 μm thick PDMS membrane is adhered across the channels.
This device allows cell cluture in a large open well format compatible with assays requireing cell scaping.
The membrane is eaisly peeled away allowing additional fixing/staining assays to be preformed and can also be repaced with a new membrane to reuse the device.

The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{Oppegard2010} and also incorporates integrated hose barbs.
The pillars extend into each well leaving a $/sim$500 $\mu$m gap for media between the diffusion membrane and the culutre surface at the bottom of the well.
Diffusion occurs rapidly across this gap allowing control of the dissolved gas environment around the cells. 
This is a prototype intended to be expanded to control all 24 wells.
A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells.
The device also features a ‘pipe within a pipe’ design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Figure \ref{fgr:well-render}.
A PDMS membrane is adhered to the microchannels of both designs by spin coating a thin PDMS layer as an adhesive.

Both devices were printed by Fineline Prototyping in Watershed XC using stereolithography.
Oxygen was measured in the 3” petri dish device with a commercial fiber-optic probe and the 24 well insert was quantified with a planar oxygen sensor as shown in Figure \ref{fig:6-well-photo}.
3D CAD models are designed and printed with microfluidic delivery channels, and then completed by adhering a gas permeable membrane of PDMS (Polydimethylsiloxane) to enable diffusion of gas to the culture area.

% Results and Discussion can be combined.
\section*{Results}

Two devices are presented and characterized: one is a large area (3” diameter) open-well format, and the second is an insert for a standard 24 well plate as shown in Figure \ref{fig:6-well-photo}.

% We only support three levels of headings, please do not create a heading level below \subsubsection.
\subsection*{Subsection 1}

\subsubsection*{SubSubsection 1.1}

\subsection*{Subsection 2}

\section*{Discussion}

\section*{Conclusion}

3D printing allows complex designs, integrated tubing connectors, and is comparable in price to standard PDMS fabrication.
This technique represents a bridge to commercialization where robust devices can be more easily shared and disseminated.
While injection molding, hot embossing, or other industrial processes are cheaper when making hundreds to thousands of devices, it is not practical to make a injection mold when making tens to hundreds of devices.
In addition, PDMS fabrication would be too time consuming, expensive, and the failure rate would be unacceptable.
3D printing is a perfect solution to these device fabrication needs.

% Do NOT remove this, even if you are not including acknowledgments.

\section*{Acknowledgments}

%\section*{References}

\bibliography{references}

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2009.bst
% style file and paste the contents of your .bbl file
% here.
%

\section*{Figure Legends}
% This section is for figure legends only, do not include
% graphics in your manuscript file.
%
%\begin{figure}
%\caption{
%{\bf Bold the first sentence.}  Rest of figure caption.  
%}
%\label{Figure_label}
%\end{figure}

\section*{Tables}
% 
% See introductory notes if you wish to include sideways tables.
%
% NOTE: Please look over our table guidelines at http://www.plosone.org/static/figureGuidelines#tables to make sure that your tables meet our requirements. Certain types of spacing, cell merging, and other formatting tricks may have unintended results and will be returned for revision.
%
%\begin{table}[!ht]
%\caption{
%\bf{Table title}}
%\begin{tabular}{|c|c|c|}
%table information
%\end{tabular}
%\begin{flushleft}Table caption
%\end{flushleft}
%\label{tab:label}
% \end{table}

\section*{Supporting Information Legends}
%
% Please enter your Supporting Information captions below in the following format:
%\item{\bf Figure SX. Enter mandatory title here.} Enter optional descriptive information here.
% 
%\begin{description}
%\item {\bf}
%\item {\bf}
%\end{description}

\end{document}

### 2015-01-14 publishing/plos_template.tex
added abstract form Utas final manuscript

@@
 
+Recently 3D printing has emerged as a method for directly printing complete microfluidic chips, 
+although printing materials have been limited to non­oxygen permeable materials.
+We demonstrate the addition of gas permeable PDMS (Polydimethylsiloxane) membranes to 3D printed microfluidic devices as a means to enable oxygen control cell culture studies.
+Two devices are presented and characterized.
+
 % Please keep the Author Summary between 150 and 200 words

### 2015-01-14 publishing/plos_template.tex
intro updated to uTAs final
oppegard citetation fixed

@@
 Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
-
-This is a test of the citations \cite{oppegard2010}.
+Two devices are demonstrated: an open-well petri dish design and a device that nests into a 24 well culture plate.
 
@@
 
-The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{Oppegard2010} and also incorporates integrated hose barbs.
+The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{oppegard2010} and also incorporates integrated hose barbs.
 The pillars extend into each well leaving a $/sim$500 $\mu$m gap for media between the diffusion membrane and the culutre surface at the bottom of the well.

### 2015-01-14 publishing/plos_template.tex
updated to final uTAS manuscript

@@
 
-The 3” petri dish device contains a 500 $\mu$m wide channel following a serpentine path leaving 500 $\mu$m of spacing between channels and has integrated hose barbs directly printed onto the device.
+The 3-inch (75 mm) petri dish device contains a 500 $\mu$m wide channel following a serpentine path leaving 500 $\mu$m of spacing between channels and has integrated hose barbs directly printed onto the device.
 The 3D part is printed with the channels embedded in the bottom of the petri dish. 
-A 120 μm thick PDMS membrane is adhered across the channels.
-This device allows cell cluture in a large open well format compatible with assays requireing cell scaping.
-The membrane is eaisly peeled away allowing additional fixing/staining assays to be preformed and can also be repaced with a new membrane to reuse the device.
+A 120 $\mu$m thick PDMS membrane is adhered across the channels by spin coating a thin layer of PDMS on the membrane and allowing it to cure in place.
+The device is designed so that a standard 3” petri dish lid may be used.
+This device allows cell culture in a large open well format compatible with assays requiring cell scraping.
+The membrane is easily peeled away allowing additional fixing/staining assays to be preformed and can also be repaced with a new membrane to reuse the device.
 
-The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{oppegard2010} and also incorporates integrated hose barbs.
-The pillars extend into each well leaving a $/sim$500 $\mu$m gap for media between the diffusion membrane and the culutre surface at the bottom of the well.
+In addition a device was designed to integrate with a multiwell format, specifically a 24 well plate. 
+The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{oppegard2010} and also incorporates integrated hose barbs to simplify device operation.
+The pillars extend into each well leaving a $\sim$500 $\mu$m gap for media between the diffusion membrane and the culutre surface at the bottom of the well.
 Diffusion occurs rapidly across this gap allowing control of the dissolved gas environment around the cells. 
-This is a prototype intended to be expanded to control all 24 wells.
 A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells.
+
 The device also features a ‘pipe within a pipe’ design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Figure \ref{fgr:well-render}.
-A PDMS membrane is adhered to the microchannels of both designs by spin coating a thin PDMS layer as an adhesive.
+Again the membranes are adhered with a thin layer of PDMS on the membrane and allowed to cure in place.
 
 Both devices were printed by Fineline Prototyping in Watershed XC using stereolithography.
-Oxygen was measured in the 3” petri dish device with a commercial fiber-optic probe and the 24 well insert was quantified with a planar oxygen sensor as shown in Figure \ref{fig:6-well-photo}.
-3D CAD models are designed and printed with microfluidic delivery channels, and then completed by adhering a gas permeable membrane of PDMS (Polydimethylsiloxane) to enable diffusion of gas to the culture area.
+CAD models were designed and printed with microfluidic delivery channels, and then completed by 
+adhering a gas permeable membrane of PDMS to enable diffusion of gas to the culture area.
 
 % Results and Discussion can be combined.
-\section*{Results}
+\section*{Results and Discussion}
 
-Two devices are presented and characterized: one is a large area (3” diameter) open-well format, and the second is an insert for a standard 24 well plate as shown in Figure \ref{fig:6-well-photo}.
+Oxygen was measured in the 3” petri dish device with a commercial fiber­optic probe (Figure 2).
+Oxygen control was demonstrated with gas flowing through the channel under the PDMS membrane.
+
+The 24 well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor as shown in Figure 2.
+Oxygen control was able to be controlled in each of the 6 wells equally from one gas input demonstrating the distribution network.
+The device depletes the wells of oxygen for 30 minutes and can then hold the oxygen level near 0\% indefinitely, while 100\% nitrogen is pumped through the device.
 
@@
 
-\section*{Discussion}
+%\section*{Discussion}
 
 \section*{Conclusion}
-
+3D printing microfluidic chips have been limited to non oxygen permeable materials.
+We demonstrate oxygen control in 3D printed devices the addition of a gas permeable PDMS membrane. 
+Oxygen control is demonstrated in a open well petri dish design and a 24 well plate.
 3D printing allows complex designs, integrated tubing connectors, and is comparable in price to standard PDMS fabrication.
@@
 \section*{Acknowledgments}
+
+This work funded by NSF 1253060.
 

### 2015-01-14 publishing/plos_template.tex
authors entered

@@
 \\
-Author1$^{1}$, 
-Author2$^{2}$, 
-Author3$^{3,\ast}$
+Martin D. Brennan$^{1}$, 
+Megan L. Rexius-Hall$^{1}$, 
+David T. Eddington$^{1,\ast}$
 \\
-\bf{1} Author1 Dept/Program/Center, Institution Name, City, State, Country
+\bf{1} Dept of Bioengineering, University of Illinois at Chicago, Chicago, Illinois, USA
 \\
-\bf{2} Author2 Dept/Program/Center, Institution Name, City, State, Country
-\\
-\bf{3} Author3 Dept/Program/Center, Institution Name, City, State, Country
-\\
-$\ast$ E-mail: Corresponding author@institute.edu
+%\bf{2} Author2 Dept/Program/Center, Institution Name, City, State, Country
+%\\
+%\bf{3} Author3 Dept/Program/Center, Institution Name, City, State, Country
+%\\
+$\ast$ E-mail: Corresponding dte@uic.edu
 \end{flushleft}

### 2015-01-16 publishing/plos_template.tex
added title
added graphicx package and figure
caption added for figure 1
added photos of device

@@
 
+\usepackage{graphicx}
+
 % amsmath package, useful for mathematical formulas
@@
 {\Large
-\textbf{Title}
+\textbf{3D-Printed Oxygen Control Devices}
 }
@@
 
+% copy and paste for figures
+%\begin{figure}
+%\includegraphics[scale=0.2]{image.jpg} % remove for manuscript submission
+%\caption{
+%{\bf Bold the first sentence.}  Rest of figure caption.  
+%}
+%\label{Figure_label}
+%\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.2]{../presentation-figures/piller-well-render-with-arrows.png} % remove for manuscript submission
+\caption{
+{\bf CAD rendering of the piller bottom.} The 'Pipe with in a pipe' flow pattern delivers gas to the bottom of each well where it diffuses to the culture.  
+}
+\label{piller-well-render-figure}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.05]{../presentation-figures/24well.JPG} % remove for manuscript submission
+\includegraphics[scale=0.05]{../presentation-figures/printed-network.JPG} % remove for manuscript submission
+\caption{
+{\bf Photographs of the printed device.}  The printed device with membranes adhered. The distribution network is printed completely in resin.
+}
+\label{Figure_label}
+\end{figure}
+
 \section*{Tables}

### 2015-01-16 publishing/plos_template.tex
figure and caption added for oxygen data

@@
 
+\begin{figure}
+\includegraphics[scale=0.3]{../presentation-figures/6-well-plot.png} % remove for manuscript submission
+\includegraphics[scale=0.3]{../presentation-figures/24-well-plot.png} % remove for manuscript submission
+\caption{
+{\bf Oxygen Characterization.}  Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device.
+Each 6 well row of the plate can be controlled independently.
+}
+\label{Figure_label}
+\end{figure}
+
 \section*{Tables}

### 2015-01-16 publishing/plos_template.tex
added caption for pcr data and fixed figure labels
added chracterization methods and cell culture title updated outline

@@
 
+\subsection*{Oxygen characterization}
+
+Oxygen was measured with PtOEPK planar sensors that were fixed to the bottom of a 24well plate. 
+The intensity of the sensor was measured and corellated to the concentration of oxygen with Stern-Volmer analysis.
+Gas was perfused through the device with negitave pressure to eliminate bubbles.
+The inlet tubing was placed in a cone with with a flow that exceded the vacuum flow rate.
+All gas tanks used in the oxygen characterization were 5\% CO2 in addition to the desired gas mix in anticipation of cell culture experiments.
+
+\subsection*{Cell culture and hypoxia assay}
+
 % Results and Discussion can be combined.
@@
 }
-\label{Figure_label}
+\label{device-photos-figure}
 \end{figure}
@@
 }
-\label{Figure_label}
+\label{oxygen-char-figure}
+\end{figure}
+
+\begin{figure}
+%\includegraphics[scale=0.2]{image.jpg} % remove for manuscript submission
+\caption{
+{\bf PCR Data.}  Not finished yet.  
+}
+\label{pcr-data}
 \end{figure}

### 2015-01-16 publishing/plos_template.tex
commented out 3 inch

@@
 We demonstrate the addition of gas permeable PDMS (Polydimethylsiloxane) membranes to 3D printed microfluidic devices as a means to enable oxygen control cell culture studies.
-Two devices are presented and characterized.
+%Two devices are presented and characterized.
 
@@
 On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which is outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
-Recently 3D printing has emerged as a method for directly printing complete microfluidic devices (folch, spence, that other one). 
+Recently 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014} (spence). 
 Printing is currently limited in choice of materials when compared to MEMS style fabrication. 
@@
 Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
-Two devices are demonstrated: an open-well petri dish design and a device that nests into a 24 well culture plate.
+We demonstrate a device that nests into a 24 well culture plate.
+%Two devices are demonstrated: an open-well petri dish design and a device that nests into a 24 well culture plate.
 
@@
 
-The 3-inch (75 mm) petri dish device contains a 500 $\mu$m wide channel following a serpentine path leaving 500 $\mu$m of spacing between channels and has integrated hose barbs directly printed onto the device.
-The 3D part is printed with the channels embedded in the bottom of the petri dish. 
-A 120 $\mu$m thick PDMS membrane is adhered across the channels by spin coating a thin layer of PDMS on the membrane and allowing it to cure in place.
-The device is designed so that a standard 3” petri dish lid may be used.
-This device allows cell culture in a large open well format compatible with assays requiring cell scraping.
-The membrane is easily peeled away allowing additional fixing/staining assays to be preformed and can also be repaced with a new membrane to reuse the device.
+%The 3-inch (75 mm) petri dish device contains a 500 $\mu$m wide channel following a serpentine path leaving 500 $\mu$m of spacing between channels and has integrated hose barbs directly printed onto the device.
+%The 3D part is printed with the channels embedded in the bottom of the petri dish. 
+%A 120 $\mu$m thick PDMS membrane is adhered across the channels by spin coating a thin layer of PDMS on the membrane and allowing it to cure in place.
+%The device is designed so that a standard 3” petri dish lid may be used.
+%This device allows cell culture in a large open well format compatible with assays requiring cell scraping.
+%The membrane is easily peeled away allowing additional fixing/staining assays to be preformed and can also be repaced with a new membrane to reuse the device.
 
-In addition a device was designed to integrate with a multiwell format, specifically a 24 well plate. 
+The device was designed to integrate with a multiwell format, specifically an off-the-shelf 24 well plate. 
 The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{oppegard2010} and also incorporates integrated hose barbs to simplify device operation.
@@
 Diffusion occurs rapidly across this gap allowing control of the dissolved gas environment around the cells. 
-A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells.
+A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells (Figure \ref{device-photos-figure}.
 
-The device also features a ‘pipe within a pipe’ design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Figure \ref{fgr:well-render}.
+The device also features a ‘pipe within a pipe’ design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Figure \ref{piller-well-render-figure}.
 Again the membranes are adhered with a thin layer of PDMS on the membrane and allowed to cure in place.
 
-Both devices were printed by Fineline Prototyping in Watershed XC using stereolithography.
+The device was printed by Fineline Prototyping in Watershed XC using stereolithography.
 CAD models were designed and printed with microfluidic delivery channels, and then completed by 
@@
 Oxygen was measured with PtOEPK planar sensors that were fixed to the bottom of a 24well plate. 
-The intensity of the sensor was measured and corellated to the concentration of oxygen with Stern-Volmer analysis.
+The intensity of the sensor was measured and corellated to the concentration of oxygen with Stern-Volmer analysis (Figure \ref{piller-well-render-figure}.
 Gas was perfused through the device with negitave pressure to eliminate bubbles.
@@
 
-The 24 well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor as shown in Figure 2.
+The 24 well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor as shown in Figure \ref{oxygen-char-figure}.
 Oxygen control was able to be controlled in each of the 6 wells equally from one gas input demonstrating the distribution network.
@@
 
-\begin{figure}
+\begin{figure}[H]
 \includegraphics[scale=0.2]{../presentation-figures/piller-well-render-with-arrows.png} % remove for manuscript submission
@@
 
-\begin{figure}
+\begin{figure}[H]
 \includegraphics[scale=0.05]{../presentation-figures/24well.JPG} % remove for manuscript submission
@@
 
-\begin{figure}
+\begin{figure}[H]
 \includegraphics[scale=0.3]{../presentation-figures/6-well-plot.png} % remove for manuscript submission
@@
 
-\begin{figure}
+\begin{figure}[H]
 %\includegraphics[scale=0.2]{image.jpg} % remove for manuscript submission

### 2015-01-16 publishing/plos_template.tex
spell checked and commented out rest of 3-inch

@@
 Recently 3D printing has emerged as a method for directly printing complete microfluidic chips, 
-although printing materials have been limited to non­oxygen permeable materials.
+although printing materials have been limited to non-oxygen permeable materials.
 We demonstrate the addition of gas permeable PDMS (Polydimethylsiloxane) membranes to 3D printed microfluidic devices as a means to enable oxygen control cell culture studies.
@@
 On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which is outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
-Recently 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014} (spence). 
+Recently 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014}. 
 Printing is currently limited in choice of materials when compared to MEMS style fabrication. 
@@
 %This device allows cell culture in a large open well format compatible with assays requiring cell scraping.
-%The membrane is easily peeled away allowing additional fixing/staining assays to be preformed and can also be repaced with a new membrane to reuse the device.
+%The membrane is easily peeled away allowing additional fixing/staining assays to be preformed and can also be replaced with a new membrane to reuse the device.
 
@@
 The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{oppegard2010} and also incorporates integrated hose barbs to simplify device operation.
-The pillars extend into each well leaving a $\sim$500 $\mu$m gap for media between the diffusion membrane and the culutre surface at the bottom of the well.
+The pillars extend into each well leaving a $\sim$500 $\mu$m gap for media between the diffusion membrane and the culture surface at the bottom of the well.
 Diffusion occurs rapidly across this gap allowing control of the dissolved gas environment around the cells. 
@@
 
-Oxygen was measured with PtOEPK planar sensors that were fixed to the bottom of a 24well plate. 
-The intensity of the sensor was measured and corellated to the concentration of oxygen with Stern-Volmer analysis (Figure \ref{piller-well-render-figure}.
-Gas was perfused through the device with negitave pressure to eliminate bubbles.
-The inlet tubing was placed in a cone with with a flow that exceded the vacuum flow rate.
+Oxygen was measured with PtOEPK planar sensors that were fixed to the bottom of a 24 well plate. 
+The intensity of the sensor was measured and correlated to the concentration of oxygen with Stern-Volmer analysis (Figure \ref{piller-well-render-figure}.
+Gas was perfused through the device with negative pressure to eliminate bubbles.
+The inlet tubing was placed in a cone with with a flow that exceed the vacuum flow rate.
 All gas tanks used in the oxygen characterization were 5\% CO2 in addition to the desired gas mix in anticipation of cell culture experiments.
@@
 
-Oxygen was measured in the 3” petri dish device with a commercial fiber­optic probe (Figure 2).
-Oxygen control was demonstrated with gas flowing through the channel under the PDMS membrane.
+%Oxygen was measured in the 3” petri dish device with a commercial fiber­optic probe (Figure 2).
+%Oxygen control was demonstrated with gas flowing through the channel under the PDMS membrane.
 

### 2015-01-22 publishing/plos_template.tex
added dte's edits

@@
 In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
+It is not unusual for labs to make ten microfluidic devices to guarnantee one will work properly.
 On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which is outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
-Recently 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014}. 
+3D printing also allows integration of complex geometeries not possible with planar lithograpy, such as hose barbs and leur fittings.
+Dissemination and distributed production is also vastly simplified due to easy shareing the design as a CAD file.
+Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014} (Poland guy?, UK guy?) 
 Printing is currently limited in choice of materials when compared to MEMS style fabrication. 
 As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials.
+\bf{Motovation for oxygen control, what we have done previously in oxygen and sepcificly the 6-well plate and why we need to do this with a 3D printer.
+Also a bit on negative pressure Vs.
+positive pressure.}
 Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
-We demonstrate a device that nests into a 24 well culture plate.
-%Two devices are demonstrated: an open-well petri dish design and a device that nests into a 24 well culture plate.
+We demonstrate a device that nests into a 24 well culture plate to control gas in each row of the plate independently of the incubators's condition.
 
@@
 
-Oxygen was measured with PtOEPK planar sensors that were fixed to the bottom of a 24 well plate. 
+Oxygen was measured with PtOEPK (Pt(II) Octaethylporphine ketone) planar sensors that were fixed to the bottom of a 24 well plate. 
 The intensity of the sensor was measured and correlated to the concentration of oxygen with Stern-Volmer analysis (Figure \ref{piller-well-render-figure}.
 Gas was perfused through the device with negative pressure to eliminate bubbles.
-The inlet tubing was placed in a cone with with a flow that exceed the vacuum flow rate.
-All gas tanks used in the oxygen characterization were 5\% CO2 in addition to the desired gas mix in anticipation of cell culture experiments.
+The inlet tubing was placed in a cone with with a flow that exceed the vacuum flow rate so that the vacuum was always pulling in the gas of interest and not the room air.
+All gas tanks used in the oxygen characterization were 5\% CO2 in addition to the desired gas mix in anticipation of cell culture experiments as CO2 can alter the fluorescence of the PtOEPK.
 
@@
 Oxygen control was able to be controlled in each of the 6 wells equally from one gas input demonstrating the distribution network.
-The device depletes the wells of oxygen for 30 minutes and can then hold the oxygen level near 0\% indefinitely, while 100\% nitrogen is pumped through the device.
+The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% indefinitely, while 100\% nitrogen is pumped through the device. 
+\bf{reach different levels.}
 

### 2015-01-22 publishing/plos_template.tex
seprated figures into second latex.tex

@@
 \documentclass[10pt]{article}
-
-\usepackage{graphicx}
 
@@
 
-\begin{figure}[H]
-\includegraphics[scale=0.2]{../presentation-figures/piller-well-render-with-arrows.png} % remove for manuscript submission
+\begin{figure}
+%\includegraphics[scale=0.2]{../presentation-figures/piller-well-render-with-arrows.png} % remove for manuscript submission
 \caption{
@@
 
-\begin{figure}[H]
-\includegraphics[scale=0.05]{../presentation-figures/24well.JPG} % remove for manuscript submission
-\includegraphics[scale=0.05]{../presentation-figures/printed-network.JPG} % remove for manuscript submission
+\begin{figure}
+%\includegraphics[scale=0.05]{../presentation-figures/24well.JPG} % remove for manuscript submission
+%\includegraphics[scale=0.05]{../presentation-figures/printed-network.JPG} % remove for manuscript submission
 \caption{
@@
 
-\begin{figure}[H]
-\includegraphics[scale=0.3]{../presentation-figures/6-well-plot.png} % remove for manuscript submission
-\includegraphics[scale=0.3]{../presentation-figures/24-well-plot.png} % remove for manuscript submission
+\begin{figure}
+%\includegraphics[scale=0.3]{../presentation-figures/6-well-plot.png} % remove for manuscript submission
+%\includegraphics[scale=0.3]{../presentation-figures/24-well-plot.png} % remove for manuscript submission
 \caption{
@@
 
-\begin{figure}[H]
+\begin{figure}
 %\includegraphics[scale=0.2]{image.jpg} % remove for manuscript submission

### 2015-01-23 publishing/plos_template.tex
worked on intro

@@
 As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials.
+Microfluidic cell culture devices are often made out of gas periable PDMS via soft photo lithography.
+PDMS is a convient material for cell studies due to it's biocompatability, optical properties, and gas periability, faciliataing oxygen control of cell environments.
+Oxygen control in cells studies is often overlooked by researchers, but important for mimicing conditions expericend by cells in vivo.
+
+Oxygen control mulitwell inserts have been previously developed cast entirely from PDMS for 6 well culture plates. \cite{Oppegard2009, Oppegard2010}.
+For a similar design to be scaled scaled (replicated) to a 24-well plate the fabriation becomes to tedious and error prone to be done by hand.
+Moveing to 3D printing for the fabrication allowed futher features to be incoporated such as integrated distubtion channels and hose barbs, while elminating fabrication time and yeild.
+Although avalible 3D pritable materials are non-gas-permiable, the addition of a PDMS membrane allows gas transfer. 
+The previous 6-well PDMS device featured paralene coating to eliminate exchange of gas in th PDMS bulk. 
 \bf{Motovation for oxygen control, what we have done previously in oxygen and sepcificly the 6-well plate and why we need to do this with a 3D printer.
 Also a bit on negative pressure Vs.
-positive pressure.}
+positive pressure.
+- I don't have any data or any reason that I can prove for doing this.
+I was orginally afraid that the membranes would come off from the pressure.
 Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.

### 2015-01-23 publishing/latex/figures.tex
organized publishing folder, added dist network rendering

--- 2015-01-22 publishing/plos_template.tex
@@
-% Template for PLoS
-% Version 2.0 July 2014
-%
-% To compile to pdf, run:
-% latex plos.template
-% bibtex plos.template
-% latex plos.template
-% latex plos.template
-% dvipdf plos.template
-%
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% Be advised that this is merely a template 
-% designed to facilitate accurate translation of manuscript content 
-% into our production files. 
-%
-% This template contains extensive comments intended 
-% to minimize problems and delays during our production 
-% process. Please follow the template 
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Once your paper is accepted for publication and enters production, 
-% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
-% the final text of your manuscript.
-%
-% DO NOT ADD EXTRA PACKAGES TO THIS TEMPLATE unless absolutely necessary.
-% Packages included in this template are intentionally
-% limited and basic in order to reduce the possibility
-% of issues during our production process.
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file. 
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - tabs/spacing/line breaks within cells to alter layout
-% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
-% - colors, shading, or graphic objects
-% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
-%
-% For sideways tables, use the {rotating} package and use \begin{sidewaystable} instead of \begin{table} in the appropriate section. PLOS guidelines do not accomodate sideways figures.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
-%
-% Please be sure to include all portions of an equation in the math environment, and for any superscripts or subscripts also include the base number/text.
-For example, use $mathrm{mm}^2$ instead of mm$^2$ (do not use \textsuperscript command).
-%
-% DO NOT USE the \rm command to render mathmode characters in roman font, instead use $\mathrm{}$
-% For bolding characters in mathmode, please use $\mathbf{}$ 
-%
-% Please add line breaks to long equations when possible in order to fit our 2-column layout. 
-%
-% For inline equations, please do not include punctuation within the math environment unless this is part of the equation.
-%
-% For spaces within the math environment please use the \; or \: commands, even within \text{} (do not use smaller spacing as this does not convert well).
-%
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-
-\documentclass[10pt]{article}
+\documentclass[]{article}
 
@@
 
-% amsmath package, useful for mathematical formulas
-\usepackage{amsmath}
-% amssymb package, useful for mathematical symbols
-\usepackage{amssymb}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-\usepackage{hyperref}
-
-% line numbers
-\usepackage{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% rotating package for sideways tables
-%\usepackage{rotating}
-
-% If you wish to include algorithms, please use one of the packages below.
-Also, please see the algorithm section of our LaTeX guidelines (http://www.plosone.org/static/latexGuidelines) for important information about required formatting.
-%\usepackage{algorithmic}
-%\usepackage{algorithmicx}
-
-% Use doublespacing - comment out for single spacing
-%\usepackage{setspace} 
-%\doublespacing
-
-% Text layout
-\topmargin 0.0cm
-\oddsidemargin 0.5cm
-\evensidemargin 0.5cm
-\textwidth 16cm 
-\textheight 21cm
-
-% Bold the 'Figure #' in the caption and separate it with a period
-% Captions will be left justified
-\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}
-
-% Use the PLoS provided BiBTeX style
-\bibliographystyle{plos2009}
-
-% Remove brackets from numbering in List of References
-\makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
-
-% Leave date blank
-\date{}
-
-\pagestyle{myheadings}
-
-%% Include all macros below. Please limit the use of macros.
-
-%% END MACROS SECTION
+%opening
+\title{Figures for  3-D printed oxygen devices}
+\author{}
 
@@
 
-% Title must be 150 characters or less
-\begin{flushleft}
-{\Large
-\textbf{3D-Printed Oxygen Control Devices}
-}
-% Insert Author names, affiliations and corresponding author email.
-\\
-Martin D. Brennan$^{1}$, 
-Megan L. Rexius-Hall$^{1}$, 
-David T. Eddington$^{1,\ast}$
-\\
-\bf{1} Dept of Bioengineering, University of Illinois at Chicago, Chicago, Illinois, USA
-\\
-%\bf{2} Author2 Dept/Program/Center, Institution Name, City, State, Country
-%\\
-%\bf{3} Author3 Dept/Program/Center, Institution Name, City, State, Country
-%\\
-$\ast$ E-mail: Corresponding dte@uic.edu
-\end{flushleft}
+%\maketitle
 
-% Please keep the abstract between 250 and 300 words
-\section*{Abstract}
-
-Recently 3D printing has emerged as a method for directly printing complete microfluidic chips, 
-although printing materials have been limited to non-oxygen permeable materials.
-We demonstrate the addition of gas permeable PDMS (Polydimethylsiloxane) membranes to 3D printed microfluidic devices as a means to enable oxygen control cell culture studies.
-%Two devices are presented and characterized.
-
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-\section*{Author Summary}
-
-\section*{Introduction}
-
-3D printing of microfluidic devices enables rapid, one-step fabrication of complex designs infeasible to make with planar lithography and replica molding techniques.
-In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
-It is not unusual for labs to make ten microfluidic devices to guarnantee one will work properly.
-On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which is outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
-3D printing also allows integration of complex geometeries not possible with planar lithograpy, such as hose barbs and leur fittings.
-Dissemination and distributed production is also vastly simplified due to easy shareing the design as a CAD file.
-Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014} (Poland guy?, UK guy?) 
-Printing is currently limited in choice of materials when compared to MEMS style fabrication. 
-As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials.
-\bf{Motovation for oxygen control, what we have done previously in oxygen and sepcificly the 6-well plate and why we need to do this with a 3D printer.
-Also a bit on negative pressure Vs.
-positive pressure.}
-Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
-We demonstrate a device that nests into a 24 well culture plate to control gas in each row of the plate independently of the incubators's condition.
-
-% You may title this section "Methods" or "Models". 
-% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
-% authors may use "Analysis" 
-\section*{Materials and Methods}
-
-%The 3-inch (75 mm) petri dish device contains a 500 $\mu$m wide channel following a serpentine path leaving 500 $\mu$m of spacing between channels and has integrated hose barbs directly printed onto the device.
-%The 3D part is printed with the channels embedded in the bottom of the petri dish. 
-%A 120 $\mu$m thick PDMS membrane is adhered across the channels by spin coating a thin layer of PDMS on the membrane and allowing it to cure in place.
-%The device is designed so that a standard 3” petri dish lid may be used.
-%This device allows cell culture in a large open well format compatible with assays requiring cell scraping.
-%The membrane is easily peeled away allowing additional fixing/staining assays to be preformed and can also be replaced with a new membrane to reuse the device.
-
-The device was designed to integrate with a multiwell format, specifically an off-the-shelf 24 well plate. 
-The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{oppegard2010} and also incorporates integrated hose barbs to simplify device operation.
-The pillars extend into each well leaving a $\sim$500 $\mu$m gap for media between the diffusion membrane and the culture surface at the bottom of the well.
-Diffusion occurs rapidly across this gap allowing control of the dissolved gas environment around the cells. 
-A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells (Figure \ref{device-photos-figure}.
-
-The device also features a ‘pipe within a pipe’ design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Figure \ref{piller-well-render-figure}.
-Again the membranes are adhered with a thin layer of PDMS on the membrane and allowed to cure in place.
-
-The device was printed by Fineline Prototyping in Watershed XC using stereolithography.
-CAD models were designed and printed with microfluidic delivery channels, and then completed by 
-adhering a gas permeable membrane of PDMS to enable diffusion of gas to the culture area.
-
-\subsection*{Oxygen characterization}
-
-Oxygen was measured with PtOEPK (Pt(II) Octaethylporphine ketone) planar sensors that were fixed to the bottom of a 24 well plate. 
-The intensity of the sensor was measured and correlated to the concentration of oxygen with Stern-Volmer analysis (Figure \ref{piller-well-render-figure}.
-Gas was perfused through the device with negative pressure to eliminate bubbles.
-The inlet tubing was placed in a cone with with a flow that exceed the vacuum flow rate so that the vacuum was always pulling in the gas of interest and not the room air.
-All gas tanks used in the oxygen characterization were 5\% CO2 in addition to the desired gas mix in anticipation of cell culture experiments as CO2 can alter the fluorescence of the PtOEPK.
-
-\subsection*{Cell culture and hypoxia assay}
-
-% Results and Discussion can be combined.
-\section*{Results and Discussion}
-
-%Oxygen was measured in the 3” petri dish device with a commercial fiber­optic probe (Figure 2).
-%Oxygen control was demonstrated with gas flowing through the channel under the PDMS membrane.
-
-The 24 well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor as shown in Figure \ref{oxygen-char-figure}.
-Oxygen control was able to be controlled in each of the 6 wells equally from one gas input demonstrating the distribution network.
-The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% indefinitely, while 100\% nitrogen is pumped through the device. 
-\bf{reach different levels.}
-
-% We only support three levels of headings, please do not create a heading level below \subsubsection.
-\subsection*{Subsection 1}
-
-\subsubsection*{SubSubsection 1.1}
-
-\subsection*{Subsection 2}
-
-%\section*{Discussion}
-
-\section*{Conclusion}
-3D printing microfluidic chips have been limited to non oxygen permeable materials.
-We demonstrate oxygen control in 3D printed devices the addition of a gas permeable PDMS membrane. 
-Oxygen control is demonstrated in a open well petri dish design and a 24 well plate.
-3D printing allows complex designs, integrated tubing connectors, and is comparable in price to standard PDMS fabrication.
-This technique represents a bridge to commercialization where robust devices can be more easily shared and disseminated.
-While injection molding, hot embossing, or other industrial processes are cheaper when making hundreds to thousands of devices, it is not practical to make a injection mold when making tens to hundreds of devices.
-In addition, PDMS fabrication would be too time consuming, expensive, and the failure rate would be unacceptable.
-3D printing is a perfect solution to these device fabrication needs.
-
-% Do NOT remove this, even if you are not including acknowledgments.
-
-\section*{Acknowledgments}
-
-This work funded by NSF 1253060.
-
-%\section*{References}
-
-\bibliography{references}
-
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% OR
-%
-% Compile your BiBTeX database using our plos2009.bst
-% style file and paste the contents of your .bbl file
-% here.
-%
-
-\section*{Figure Legends}
-% This section is for figure legends only, do not include
-% graphics in your manuscript file.
-%
-%\begin{figure}
-%\caption{
-%{\bf Bold the first sentence.}  Rest of figure caption.  
-%}
-%\label{Figure_label}
-%\end{figure}
-
-% copy and paste for figures
-%\begin{figure}
-%\includegraphics[scale=0.2]{image.jpg} % remove for manuscript submission
-%\caption{
-%{\bf Bold the first sentence.}  Rest of figure caption.  
-%}
-%\label{Figure_label}
-%\end{figure}
+\section{figures}
 
@@
 
-\section*{Tables}
-% 
-% See introductory notes if you wish to include sideways tables.
-%
-% NOTE: Please look over our table guidelines at http://www.plosone.org/static/figureGuidelines#tables to make sure that your tables meet our requirements.
-Certain types of spacing, cell merging, and other formatting tricks may have unintended results and will be returned for revision.
-%
-%\begin{table}[!ht]
-%\caption{
-%\bf{Table title}}
-%\begin{tabular}{|c|c|c|}
-%table information
-%\end{tabular}
-%\begin{flushleft}Table caption
-%\end{flushleft}
-%\label{tab:label}
-% \end{table}
+%\begin{abstract}
 
-\section*{Supporting Information Legends}
-%
-% Please enter your Supporting Information captions below in the following format:
-%\item{\bf Figure SX. Enter mandatory title here.} Enter optional descriptive information here.
-% 
-%\begin{description}
-%\item {\bf}
-%\item {\bf}
-%\end{description}
+%\end{abstract}
+
+%\section{}
 

### 2015-01-26 publishing/latex/figures.tex
updated figure1 and outline

@@
 \begin{figure}[H]
-\includegraphics[scale=0.2]{../presentation-figures/piller-well-render-with-arrows.png} % remove for manuscript submission
+\includegraphics[scale=0.2]{fig1.png} 
 \caption{
-{\bf CAD rendering of the piller bottom.} The 'Pipe with in a pipe' flow pattern delivers gas to the bottom of each well where it diffuses to the culture.  
+{\bf 24-well Insert Device.} A microfluidic network distributes gas flow from one hose barb input to 6 wells.
+A 'Pipe with in a pipe' design delivers gas to the bottom of each well where it diffuses to the culture through an adhered PDMS membrane (blue-layer).  
+The distribution network width of the channels in the distribution network are such that the flow rates are equalized to each well dependent on the path length.
 }
-\label{piller-well-render-figure}
+\label{figure1}
 \end{figure}
 
-\begin{figure}[H]
-\includegraphics[scale=0.05]{../presentation-figures/24well.JPG} % remove for manuscript submission
-\includegraphics[scale=0.05]{../presentation-figures/printed-network.JPG} % remove for manuscript submission
-\caption{
-{\bf Photographs of the printed device.}  The printed device with membranes adhered. The distribution network is printed completely in resin.
-}
-\label{device-photos-figure}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[scale=0.3]{../presentation-figures/6-well-plot.png} % remove for manuscript submission
-\includegraphics[scale=0.3]{../presentation-figures/24-well-plot.png} % remove for manuscript submission
-\caption{
-{\bf Oxygen Characterization.}  Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device.
+%\begin{figure}[H]
+%\includegraphics[scale=0.3]{../presentation-figures/6-well-plot.png} % remove for manuscript submission
+%\includegraphics[scale=0.3]{../presentation-figures/24-well-plot.png} % remove for manuscript submission
+%\caption{
+%{\bf Oxygen Characterization.}  Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device.
 Each 6 well row of the plate can be controlled independently.
-}
-\label{oxygen-char-figure}
-\end{figure}
+%}
+%\label{oxygen-char-figure}
+%\end{figure}
 

### 2015-01-26 publishing/latex/plos_template.tex
added more intro

--- 2015-01-23 publishing/plos_template.tex
@@
 As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials.
-Microfluidic cell culture devices are often made out of gas periable PDMS via soft photo lithography.
+
+Microfluidic cell culture devices are often made out of PDMS via soft photo lithography.
 PDMS is a convient material for cell studies due to it's biocompatability, optical properties, and gas periability, faciliataing oxygen control of cell environments.
+
 Oxygen control in cells studies is often overlooked by researchers, but important for mimicing conditions expericend by cells in vivo.
+Typically cell culture studies are preformed at 21\% oxygen, atmospheric oxygen conditions, although levels that cells experience in vivo are usually less.
+For example tumors, in gereral, are hypoxic as they rapidly out grow their vasculature creating a hypoxic inner region. 
+To better study the role of oxygen levels in cancer gene expression a gas controled culture system is required.
 
-Oxygen control mulitwell inserts have been previously developed cast entirely from PDMS for 6 well culture plates. \cite{Oppegard2009, Oppegard2010}.
-For a similar design to be scaled scaled (replicated) to a 24-well plate the fabriation becomes to tedious and error prone to be done by hand.
-Moveing to 3D printing for the fabrication allowed futher features to be incoporated such as integrated distubtion channels and hose barbs, while elminating fabrication time and yeild.
+Oxygen control mulitwell inserts have been previously developed, which were cast entirely from PDMS, for 6 well culture plates. \cite{Oppegard2009, Oppegard2010}.
+To replicate the 6-well design for a 24 well format the fabriation via PDMS casting becomes too tedious and to be done by hand and has a high failure rate.
+Utilizing 3D printing for the fabrication allowed futher features to be incoporated such as integrated distubtion channels and hose barbs, while elminating fabrication time and failure rate.
 Although avalible 3D pritable materials are non-gas-permiable, the addition of a PDMS membrane allows gas transfer. 
-The previous 6-well PDMS device featured paralene coating to eliminate exchange of gas in th PDMS bulk. 
+In this case, having a non-gas-permaible material for the bulk is advantagous as it acts as a insulator to gas transfer. 
+Convection and distribution of the gas is done in the non-permiable material eliminating dilution of the gas before reaching the diffusion layer. 
+The previous PDMS devices were paralene coated along the convection channels to eliminate exchange of gas from the PDMS bulk.
+
 \bf{Motovation for oxygen control, what we have done previously in oxygen and sepcificly the 6-well plate and why we need to do this with a 3D printer.
@@
 - I don't have any data or any reason that I can prove for doing this.
-I was orginally afraid that the membranes would come off from the pressure.
+I was orginally afraid that the membranes would come off from the pressure, I am testing it now.
+
 Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
@@
 
+\subsection*{Design of Insert}
+
 The device was designed to integrate with a multiwell format, specifically an off-the-shelf 24 well plate. 
-The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{oppegard2010} and also incorporates integrated hose barbs to simplify device operation.
+The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{oppegard2010} and also incorporates an integrated distribution network and hose barbs to simplify device operation.
 The pillars extend into each well leaving a $\sim$500 $\mu$m gap for media between the diffusion membrane and the culture surface at the bottom of the well.
 Diffusion occurs rapidly across this gap allowing control of the dissolved gas environment around the cells. 
-A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells (Figure \ref{device-photos-figure}.
+A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells (Figure \ref{figure1}.
 
-The device also features a ‘pipe within a pipe’ design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Figure \ref{piller-well-render-figure}.
+The device also features a ‘pipe within a pipe’ design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Figure \ref{figure1}.
 Again the membranes are adhered with a thin layer of PDMS on the membrane and allowed to cure in place.

### 2015-01-26 publishing/latex/plos_template.tex
updated paper and bib

@@
 In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
-It is not unusual for labs to make ten microfluidic devices to guarnantee one will work properly.
+It is not unusual for labs to make ten microfluidic devices to guarantee one will work properly.
 On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which is outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
-3D printing also allows integration of complex geometeries not possible with planar lithograpy, such as hose barbs and leur fittings.
-Dissemination and distributed production is also vastly simplified due to easy shareing the design as a CAD file.
-Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014} (Poland guy?, UK guy?) 
+3D printing also allows integration of complex geometries not possible with planar lithography, such as hose barbs and luer fittings.
+Dissemination and distributed production is also vastly simplified due to easy sharing the design as a CAD file.
+Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014, Shallan2014,Erkal2014,Kitson2014}. 
 Printing is currently limited in choice of materials when compared to MEMS style fabrication. 
@@
 Microfluidic cell culture devices are often made out of PDMS via soft photo lithography.
-PDMS is a convient material for cell studies due to it's biocompatability, optical properties, and gas periability, faciliataing oxygen control of cell environments.
+PDMS is a convenient material for cell studies due to it's biocompatibility, optical properties, and gas permeability, facilitating oxygen control of cell environments.
 
-Oxygen control in cells studies is often overlooked by researchers, but important for mimicing conditions expericend by cells in vivo.
+Oxygen control in cells studies is often overlooked by researchers, but important for mimicking conditions experienced by cells in vivo.
 Typically cell culture studies are preformed at 21\% oxygen, atmospheric oxygen conditions, although levels that cells experience in vivo are usually less.
-For example tumors, in gereral, are hypoxic as they rapidly out grow their vasculature creating a hypoxic inner region. 
-To better study the role of oxygen levels in cancer gene expression a gas controled culture system is required.
+For example tumors, in general, are hypoxic as they rapidly out grow their vasculature creating a hypoxic inner region. 
+To better study the role of oxygen levels in cancer gene expression a gas controlled culture system is required.
 
 Oxygen control mulitwell inserts have been previously developed, which were cast entirely from PDMS, for 6 well culture plates. \cite{Oppegard2009, Oppegard2010}.
-To replicate the 6-well design for a 24 well format the fabriation via PDMS casting becomes too tedious and to be done by hand and has a high failure rate.
-Utilizing 3D printing for the fabrication allowed futher features to be incoporated such as integrated distubtion channels and hose barbs, while elminating fabrication time and failure rate.
-Although avalible 3D pritable materials are non-gas-permiable, the addition of a PDMS membrane allows gas transfer. 
-In this case, having a non-gas-permaible material for the bulk is advantagous as it acts as a insulator to gas transfer. 
-Convection and distribution of the gas is done in the non-permiable material eliminating dilution of the gas before reaching the diffusion layer. 
-The previous PDMS devices were paralene coated along the convection channels to eliminate exchange of gas from the PDMS bulk.
+To replicate the 6-well design for a 24 well format the fabrication via PDMS casting becomes too tedious and to be done by hand and has a high failure rate.
+Utilizing 3D printing for the fabrication allowed further features to be incorporated such as integrated distribution channels and hose barbs, while eliminating fabrication time and failure rate.
+Although available 3D printable materials are non-gas-permeable, the addition of a PDMS membrane allows gas transfer. 
+In this case, having a non-gas-permeable material for the bulk is advantageous as it acts as a insulator to gas transfer. 
+Convection and distribution of the gas is done in the non-permeable material eliminating dilution of the gas before reaching the diffusion layer. 
+The previous PDMS devices were parylene coated along the convection channels to eliminate exchange of gas from the PDMS bulk.
 
-\bf{Motovation for oxygen control, what we have done previously in oxygen and sepcificly the 6-well plate and why we need to do this with a 3D printer.
+---Motovation for oxygen control, what we have done previously in oxygen and sepcificly the 6-well plate and why we need to do this with a 3D printer.
 Also a bit on negative pressure Vs.
@@
 - I don't have any data or any reason that I can prove for doing this.
-I was orginally afraid that the membranes would come off from the pressure, I am testing it now.
+I was orginally afraid that the membranes would come off from the pressure, I am testing it now.---
 
 Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
-We demonstrate a device that nests into a 24 well culture plate to control gas in each row of the plate independently of the incubators's condition.
+We demonstrate a device that nests into a 24 well culture plate to control gas in each row of the plate independently of the incubator's condition.
 

### 2015-02-06 publishing/latex/plos_template.tex
added dte's edits, and updated outline plan

@@
 {\Large
-\textbf{3D-Printed Oxygen Control Devices}
+\textbf{3D-Printed Microfluidic Oxygen Control Devices}
 }
@@
 
+Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
+We demonstrate a device that nests into a 24 well culture plate to control gas in each row of the plate independently of the incubator's condition.
+
 3D printing of microfluidic devices enables rapid, one-step fabrication of complex designs infeasible to make with planar lithography and replica molding techniques.
 In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
-It is not unusual for labs to make ten microfluidic devices to guarantee one will work properly.
-On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which is outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
+It is not unusual for microfluidic labs to make ten microfluidic devices to guarantee one will work properly.
+On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which may be outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
 3D printing also allows integration of complex geometries not possible with planar lithography, such as hose barbs and luer fittings.
-Dissemination and distributed production is also vastly simplified due to easy sharing the design as a CAD file.
+Dissemination and distributed production is also vastly simplified due to easy sharing of the design as a CAD file.
+Microfluidic 3D printed devices have been used in XYZ.
 Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014, Shallan2014,Erkal2014,Kitson2014}. 
@@
 
-Microfluidic cell culture devices are often made out of PDMS via soft photo lithography.
+Microfluidic cell culture devices are typically cast in PDMS.
 PDMS is a convenient material for cell studies due to it's biocompatibility, optical properties, and gas permeability, facilitating oxygen control of cell environments.
@@
 
-Oxygen control mulitwell inserts have been previously developed, which were cast entirely from PDMS, for 6 well culture plates. \cite{Oppegard2009, Oppegard2010}.
-To replicate the 6-well design for a 24 well format the fabrication via PDMS casting becomes too tedious and to be done by hand and has a high failure rate.
-Utilizing 3D printing for the fabrication allowed further features to be incorporated such as integrated distribution channels and hose barbs, while eliminating fabrication time and failure rate.
-Although available 3D printable materials are non-gas-permeable, the addition of a PDMS membrane allows gas transfer. 
-In this case, having a non-gas-permeable material for the bulk is advantageous as it acts as a insulator to gas transfer. 
-Convection and distribution of the gas is done in the non-permeable material eliminating dilution of the gas before reaching the diffusion layer. 
-The previous PDMS devices were parylene coated along the convection channels to eliminate exchange of gas from the PDMS bulk.
-
----Motovation for oxygen control, what we have done previously in oxygen and sepcificly the 6-well plate and why we need to do this with a 3D printer.
-Also a bit on negative pressure Vs.
-positive pressure.
-- I don't have any data or any reason that I can prove for doing this.
-I was orginally afraid that the membranes would come off from the pressure, I am testing it now.---
-
-Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
-We demonstrate a device that nests into a 24 well culture plate to control gas in each row of the plate independently of the incubator's condition.
+Previously, we developed multiwell inserts for 6-well plates that controlled oxygen in a standard off-the self plate \cite{Oppegard2009, Oppegard2010}.
+These devices were completely cast from PDMS and fabricated in a multiple bonding procedure.
+In addition, tubing was used to connect each pillar which became quite cumbersome when moving to a newer 24-well version.
+Utilizing 3D printing for the fabrication allowed further features to be incorporated such as integrated distribution channels to eliminate the connection tubings between wells and hose barbs for better tubing connections, while eliminating fabrication time and failure rate.
+Although available 3D printable materials are non-gas-permeable, the addition of a PDMS membrane following printing the passive microfluidic network is a simple addition allowing gas transfer. 
+In this case, having a gas-impermeable material for the bulk is advantageous as it reduces unwanted gas transfer. 
+The previous PDMS devices were parylene coated along the convection channels to eliminate exchange of gas from the PDMS bulk, which again added to their complexity and is now longer needed.
+Convection and distribution of the gas is done in the impermeable material eliminating dilution of the gas before reaching the diffusion layer.
 

### 2015-02-06 publishing/latex/plos_template.tex
added rendering and updated manuscript

@@
 We demonstrate the addition of gas permeable PDMS (Polydimethylsiloxane) membranes to 3D printed microfluidic devices as a means to enable oxygen control cell culture studies.
+With this device oxygen was able to be controlled to 4 different conditions across a 24 well plate demonstrating regulation of oxygen sentsive transcripional protien in cancer cells.
+This is the first 3D printed device that can be functionalized to control oxygen in cell culture.
 %Two devices are presented and characterized.
@@
 Microfluidic 3D printed devices have been used in XYZ.
+Many quintessential microfluidic devices and features have been recreated with 3D printing as a proof of concept for this new fabrication technique \cite{Au2014, Shallan2014}.
+3D printed devices have been used for inexpensive and high-throughput reactionware,\cite{Kitson2014}, for a measureing dopamine and ATP levels in biological samples\cite{Erkal2014]. 
 Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014, Shallan2014,Erkal2014,Kitson2014}. 
-Printing is currently limited in choice of materials when compared to MEMS style fabrication. 
+Printing is currently limited in choice of materials compatable with the process and include many proprietary fomulations, regardless these have been sucessfully used in a variety of applications.
 As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials.

### 2015-02-06 publishing/latex/plos_template.tex
added whole render to figure 1 and figure labels, fixed bracket in manuscript

@@
 Many quintessential microfluidic devices and features have been recreated with 3D printing as a proof of concept for this new fabrication technique \cite{Au2014, Shallan2014}.
-3D printed devices have been used for inexpensive and high-throughput reactionware,\cite{Kitson2014}, for a measureing dopamine and ATP levels in biological samples\cite{Erkal2014]. 
+3D printed devices have been used for inexpensive and high-throughput reactionware,\cite{Kitson2014}, for a measureing dopamine and ATP levels in biological samples\cite{Erkal2014}
 Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014, Shallan2014,Erkal2014,Kitson2014}. 

### 2015-02-06 publishing/latex/figures.tex
added figure 2
added whole render, update manuscript and figures

--- 2015-01-23 publishing/latex/figures.tex
@@
 \begin{figure}[H]
-\includegraphics[scale=0.2]{../presentation-figures/piller-well-render-with-arrows.png} % remove for manuscript submission
+\includegraphics[scale=0.2]{fig1.png} 
 \caption{
-{\bf CAD rendering of the piller bottom.} The 'Pipe with in a pipe' flow pattern delivers gas to the bottom of each well where it diffuses to the culture.  
+{\bf Design of 24-well Insert Device.}
+(A) Rendering of whole 3D printed part.
+The device inserts into a standard 24 well plate.
+An inlet and oulet barb allows perfusion of gas to control 6 channels.
+The design is iterated four times for a total of 24 wells.
+(B) Cross-section demonstrating how the microfluidic distribution network and double pipes are connected. 
+The two adjacent asymentical distribution networks are spaced 1 mm apart along the z axis allowing them to overlap and enter the seperate vertical pipes.
+The arrows indicate the flow direction.
+The incoming gas enters enters the outer pipe on its way to the bottom of the well and returns through the inner pipe.
+(C) At the bottom of the pillar gas flow along the PDMS membrane (blue), which is supported by micropillars, and exits via the inner pipe.
+Diffusion occurs rapidly through the PDMS membrane to the cell culture spaced 500 $\mu$m away at the bottom of the well.
+(D) The width of the channels in the distribution network are such that the flow rates are equalized to each well dependent on the path length.
+----The empty space above (D) will have labels and arrow pointing to: membrane, micropillars, supports, inner pipe, and outer pipe.----
 }
-\label{piller-well-render-figure}
+\label{figure1}
 \end{figure}
@@
 \begin{figure}[H]
-\includegraphics[scale=0.05]{../presentation-figures/24well.JPG} % remove for manuscript submission
-\includegraphics[scale=0.05]{../presentation-figures/printed-network.JPG} % remove for manuscript submission
-\caption{
-{\bf Photographs of the printed device.}  The printed device with membranes adhered. The distribution network is printed completely in resin.
-}
-\label{device-photos-figure}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[scale=0.3]{../presentation-figures/6-well-plot.png} % remove for manuscript submission
-\includegraphics[scale=0.3]{../presentation-figures/24-well-plot.png} % remove for manuscript submission
+\includegraphics[scale=0.25]{fig2.png}
 \caption{
@@
 }
-\label{oxygen-char-figure}
+\label{figure2}
 \end{figure}

### 2015-02-06 publishing/latex/plos_template.tex
added whole render, update manuscript and figures

@@
 It is not unusual for microfluidic labs to make ten microfluidic devices to guarantee one will work properly.
-On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which may be outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
+On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which may be outsourced to a 3D printing company for around \$100/device \cite{Au2014}.
 3D printing also allows integration of complex geometries not possible with planar lithography, such as hose barbs and luer fittings.
 Dissemination and distributed production is also vastly simplified due to easy sharing of the design as a CAD file.
-Microfluidic 3D printed devices have been used in XYZ.
-Many quintessential microfluidic devices and features have been recreated with 3D printing as a proof of concept for this new fabrication technique \cite{Au2014, Shallan2014}.
-3D printed devices have been used for inexpensive and high-throughput reactionware,\cite{Kitson2014}, for a measureing dopamine and ATP levels in biological samples\cite{Erkal2014}
-Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014, Shallan2014,Erkal2014,Kitson2014}. 
+Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Shallan 2014, Chen2014, Erkal2014,Bhargava2014}. 
+Many prototypical microfluidic device features have been recreated with 3D printing as a proof of concept for this new fabrication technique \cite{Au2014, Shallan2014} including modular re-configurable units\cite{Bharagava2014}.
+3D printed devices have been used for inexpensive and high-throughput reactionware,\cite{Kitson2014}, for a measureing dopamine and ATP levels in biological samples with an integrated electrode\cite{Erkal2014}, aswell as a device that allows flow through measuments of ATP to be taken with a plate reader\cite{Chen2014}.
+
 Printing is currently limited in choice of materials compatable with the process and include many proprietary fomulations, regardless these have been sucessfully used in a variety of applications.
-As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials.
-
-Microfluidic cell culture devices are typically cast in PDMS.
+As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials although this area is being developed\cite{Femmer2014}.
+Microfluidic cell culture devices are most commonly cast in PDMS.
 PDMS is a convenient material for cell studies due to it's biocompatibility, optical properties, and gas permeability, facilitating oxygen control of cell environments.
@@
 For example tumors, in general, are hypoxic as they rapidly out grow their vasculature creating a hypoxic inner region. 
-To better study the role of oxygen levels in cancer gene expression a gas controlled culture system is required.
+To better study the role of oxygen levels in cancer gene expression a gas controlled culture system is required. ----I have to cite all this----
 
@@
 \section*{Materials and Methods}
-
-%The 3-inch (75 mm) petri dish device contains a 500 $\mu$m wide channel following a serpentine path leaving 500 $\mu$m of spacing between channels and has integrated hose barbs directly printed onto the device.
-%The 3D part is printed with the channels embedded in the bottom of the petri dish. 
-%A 120 $\mu$m thick PDMS membrane is adhered across the channels by spin coating a thin layer of PDMS on the membrane and allowing it to cure in place.
-%The device is designed so that a standard 3” petri dish lid may be used.
-%This device allows cell culture in a large open well format compatible with assays requiring cell scraping.
-%The membrane is easily peeled away allowing additional fixing/staining assays to be preformed and can also be replaced with a new membrane to reuse the device.
 

### 2015-02-06 publishing/latex/plos_template.tex
spell checked and updated references

@@
 We demonstrate the addition of gas permeable PDMS (Polydimethylsiloxane) membranes to 3D printed microfluidic devices as a means to enable oxygen control cell culture studies.
-With this device oxygen was able to be controlled to 4 different conditions across a 24 well plate demonstrating regulation of oxygen sentsive transcripional protien in cancer cells.
+With this device oxygen was able to be controlled to 4 different conditions across a 24 well plate demonstrating regulation of oxygen sensitive transcriptional protein in cancer cells.
 This is the first 3D printed device that can be functionalized to control oxygen in cell culture.
@@
 Many prototypical microfluidic device features have been recreated with 3D printing as a proof of concept for this new fabrication technique \cite{Au2014, Shallan2014} including modular re-configurable units\cite{Bharagava2014}.
-3D printed devices have been used for inexpensive and high-throughput reactionware,\cite{Kitson2014}, for a measureing dopamine and ATP levels in biological samples with an integrated electrode\cite{Erkal2014}, aswell as a device that allows flow through measuments of ATP to be taken with a plate reader\cite{Chen2014}.
+3D printed devices have been used for inexpensive and high-throughput reactionware,\cite{Kitson2014}, for a measuring dopamine and ATP levels in biological samples with an integrated electrode\cite{Erkal2014}, as well as a device that allows flow through measurements of ATP to be taken with a plate reader\cite{Chen2014}.
 
-Printing is currently limited in choice of materials compatable with the process and include many proprietary fomulations, regardless these have been sucessfully used in a variety of applications.
+Printing is currently limited in choice of materials compatible with the process and include many proprietary formulations, regardless these have been successfully used in a variety of applications.
 As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials although this area is being developed\cite{Femmer2014}.
@@
 
-The device also features a ‘pipe within a pipe’ design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Figure \ref{figure1}.
+The device also features a pipe within a pipe design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Figure \ref{figure1}.
 Again the membranes are adhered with a thin layer of PDMS on the membrane and allowed to cure in place.

### 2015-02-06 publishing/latex/figures.tex
spell checker

@@
 The device inserts into a standard 24 well plate.
-An inlet and oulet barb allows perfusion of gas to control 6 channels.
+An inlet and outlet barb allows perfusion of gas to control 6 channels.
 The design is iterated four times for a total of 24 wells.
 (B) Cross-section demonstrating how the microfluidic distribution network and double pipes are connected. 
-The two adjacent asymentical distribution networks are spaced 1 mm apart along the z axis allowing them to overlap and enter the seperate vertical pipes.
+The two adjacent mirrored distribution networks are spaced 1 mm apart along the z axis allowing them to overlap and enter the separate vertical pipes.
 The arrows indicate the flow direction.

### 2015-02-12 publishing/latex/plos_template.tex
udated with DTE's edits

@@
 
+\usepackage[version=3]{mhchem}
+
 % Text layout
@@
 We demonstrate the addition of gas permeable PDMS (Polydimethylsiloxane) membranes to 3D printed microfluidic devices as a means to enable oxygen control cell culture studies.
+This was demonstrated on an expanded 24 well version of our previous device which was for a 6-well plate.
+The direct printing allows integrated distribution channels and device geometries not possible with traditional planar lithography.
 With this device oxygen was able to be controlled to 4 different conditions across a 24 well plate demonstrating regulation of oxygen sensitive transcriptional protein in cancer cells.
@@
 We demonstrate a device that nests into a 24 well culture plate to control gas in each row of the plate independently of the incubator's condition.
+This expands on our previous work of a similar device for 6-well plates\cite{Oppegard2009,Oppegard2010}.
+The ability to independentaly control oxygen across each row of the plate enables more efficient experiments as a separate incubator or hypoxic chamber is not needed for each condition.
 
@@
 The device was printed by Fineline Prototyping in Watershed XC using stereolithography.
-CAD models were designed and printed with microfluidic delivery channels, and then completed by 
-adhering a gas permeable membrane of PDMS to enable diffusion of gas to the culture area.
+CAD models were designed and printed with microfluidic delivery channels, and then completed by adhering a gas permeable membrane of PDMS to enable diffusion of gas to the culture area using uncured PDMS as an adhesive.
 
@@
 The intensity of the sensor was measured and correlated to the concentration of oxygen with Stern-Volmer analysis (Figure \ref{piller-well-render-figure}.
-Gas was perfused through the device with negative pressure to eliminate bubbles.
+Gas was perfused through the device with negative pressure to reduce membrane debonding and was also found to reduce the number of bubbles formed in the culture chamber.
 The inlet tubing was placed in a cone with with a flow that exceed the vacuum flow rate so that the vacuum was always pulling in the gas of interest and not the room air.
@@
 
-%Oxygen was measured in the 3” petri dish device with a commercial fiber­optic probe (Figure 2).
-%Oxygen control was demonstrated with gas flowing through the channel under the PDMS membrane.
+The 24 well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor as shown in Figure \ref{oxygen-char-figure}.
+Oxygen control was able to be controlled in each of the 6 wells equally from one gas input demonstrating the distribution network worked effectively.
+The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% indefinitely, while 95\% \ce{N2}, 5\% \ce{CO2} is pumped through the device. 
+\bf{reach different levels.}
 
-The 24 well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor as shown in Figure \ref{oxygen-char-figure}.
-Oxygen control was able to be controlled in each of the 6 wells equally from one gas input demonstrating the distribution network.
-The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% indefinitely, while 100\% nitrogen is pumped through the device. 
-\bf{reach different levels.}
+mRNA stuff
+
+Future directions: more channel networks, higher format plates, stackable plates with gas connections
 
@@
 We demonstrate oxygen control in 3D printed devices the addition of a gas permeable PDMS membrane. 
-Oxygen control is demonstrated in a open well petri dish design and a 24 well plate.
+Oxygen control is demonstrated in a 24 well plate and PCR analysis of X in Y cells shows the device effectively controls oxygen as expected.
 3D printing allows complex designs, integrated tubing connectors, and is comparable in price to standard PDMS fabrication.

### 2015-02-13 publishing/latex/plos_template.tex
updated methods and discussion

@@
 All gas tanks used in the oxygen characterization were 5\% CO2 in addition to the desired gas mix in anticipation of cell culture experiments as CO2 can alter the fluorescence of the PtOEPK.
+Intensity measurments were taken every five minutes for each well.
+Initially the inlets are fed with a 5\% \ce{CO2}, bal. air tank until the intensity stableized.
+The inlets are then switched to the contol gas of either 0, 5 10 or 21\% \ce{O2}, each with 5\% \ce{CO2} and balanced with \ce{N2}.
+Intensity measurements are then taken every five minutes for six hours.
+The this entire procedure was reapeated three times for and N of three.
 
 \subsection*{Cell culture and hypoxia assay}
+
+Cancer cells were seeded in a 24 well plate.
+When they reached $\sim$70\% confluency the 24-well insert is placed in the plate and the gasses are perfused through the device in the same scheme as in the oxygen characterization.
+Each row of six wells experiences either 0, 5, 10 or 21\% \ce{O2}, with 5\% \ce{CO2} and balanced nitrogen.
+The assmebly is placed in an incubator at $37\,^{\circ}\mathrm{C}$ for six hours.
 
@@
 Oxygen control was able to be controlled in each of the 6 wells equally from one gas input demonstrating the distribution network worked effectively.
-The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% indefinitely, while 95\% \ce{N2}, 5\% \ce{CO2} is pumped through the device. 
-\bf{reach different levels.}
+The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% \ce{O2} indefinitely, while 95\% \ce{N2}, 5\% \ce{CO2} is pumped through the device. 
+A different gas condition can be used in each sepereate iteration of the 6-well unit allowing 6 tecnical replicants of up to 4 different gas conditions in one 24 well plate\ref{fig2}.
 
-mRNA stuff
+Bioverification of the devices ablility to control the gas enviroment is demonstrated with hypoxia influenced expression of mRNA in cancer cells\ref{fig3}.
+
+More mRNA stuff for megan to expand
 

### 2015-03-02 data/24-well-results/average_trials.m
plotted data for 24 well

@@ -1,0 +1,17 @@
+clear
+load n1.csv % loads data in to n1
+load n2.csv
+load n3.csv
+
+whole = zeros(142,24,3);  % makes 3D matrix to fill
+
+whole(:,:,1) = fliplr(n1);       % fills matrix with data, fliplr flips columns
+whole(:,:,2) = n2;
+whole(:,:,3) = n3;
+
+mean = mean(whole,3); % takes mean along 3rd dimension
+
+std = std(whole,0,3); % takes std along 3rd dimension
+
+save -ascii mean.csv mean
+save -ascii std.csv std

### 2015-03-02 data/24-well-results/stern24.m

@@ -1,0 +1,36 @@
+clear
+load Results120514.csv
+Results = Results120514;
+r = reshape(Results(:,3), rows(Results)/24, 24);
+%save r.csv r
+ss_mean = mean(r(1:10,:));
+amb_mean = mean(r(15:18,:));
+intensities = [ss_mean;zeros(1,columns(r));amb_mean;(ones(1,columns(r)))*21;r(11:rows(r),:)];
+
+number_of_wells = columns (intensities); % finds the number of columns in the matrix
+a = zeros (size (intensities));
+b=0;
+i=1;
+for i = 1:columns (intensities)
+   b=b+1;
+   well = intensities(:,i);
+   calibration_intensity1 = well(1);
+   calibration_intensity2 = well(3);
+   calibration_measurment1 = well(2);
+   calibration_measurment2 = well(4);
+
+kt = (calibration_intensity2-calibration_intensity1)/((calibration_measurment1*calibration_intensity1)-(calibration_measurment2*calibration_intensity2)); % calculation for Ktau
+
+I0 = (1+kt*calibration_measurment1)*calibration_intensity1; % intensity in absence of quencher(0% O2)
+
+x1 = 0:1:100;              % makes x values for plot of stern-volmer
+y1 = I0./(1+kt*x1);        % plots stern-volmer. Check to see if its fitting your calibration points.
+
+calculated_percent = ((I0./well)-1)/kt;
+a(:,i) = calculated_percent;
+
+endfor
+
+eval = a(5:rows(a),:);
+
+save -ascii evaluated120514.csv eval

### 2015-03-03 publishing/latex/figures.tex
updated tex for figures
adjusted scale for fig1
updated figures

@@
 \begin{figure}[H]
-\includegraphics[scale=0.2]{fig1.png} 
+\includegraphics[scale=.75]{fig1.png} 
 \caption{
@@
 Diffusion occurs rapidly through the PDMS membrane to the cell culture spaced 500 $\mu$m away at the bottom of the well.
-(D) The width of the channels in the distribution network are such that the flow rates are equalized to each well dependent on the path length.
+(D) 
+(E)
+(F)
 ----The empty space above (D) will have labels and arrow pointing to: membrane, micropillars, supports, inner pipe, and outer pipe.----

### 2015-03-04 publishing/latex/figures.tex
updated figures

@@
 (A) Rendering of whole 3D printed part.
-The device inserts into a standard 24 well plate.
 An inlet and outlet barb allows perfusion of gas to control 6 channels.
-The design is iterated four times for a total of 24 wells.
-(B) Cross-section demonstrating how the microfluidic distribution network and double pipes are connected. 
-The two adjacent mirrored distribution networks are spaced 1 mm apart along the z axis allowing them to overlap and enter the separate vertical pipes.
+(B) At the bottom of each pillar gas entering from the outer channel flows along the PDMS membrane (blue), which is supported by micropillars, and exhausts via the inner pipe.
+Diffusion occurs rapidly through the PDMS membrane to the cell culture spaced 500 $\mu$m away at the bottom of the well.
+(C) Cross-section demonstrating how the microfluidic distribution network and double pipes are connected. 
+The two adjacent mirrored distribution networks are spaced 1 mm apart along the z-axis allowing them to overlap and enter the separate vertical pipes.
 The arrows indicate the flow direction.
 The incoming gas enters enters the outer pipe on its way to the bottom of the well and returns through the inner pipe.
-(C) At the bottom of the pillar gas flow along the PDMS membrane (blue), which is supported by micropillars, and exits via the inner pipe.
-Diffusion occurs rapidly through the PDMS membrane to the cell culture spaced 500 $\mu$m away at the bottom of the well.
-(D) 
-(E)
-(F)
-----The empty space above (D) will have labels and arrow pointing to: membrane, micropillars, supports, inner pipe, and outer pipe.----
+(D) Photo of the device with dyed channels in a 24-well plate.
+(E) Photo of the device from the bottom with four independent channel networks.
+(F) Photo of the printed distrubution networks.
 }
@@
 \begin{figure}[H]
-\includegraphics[scale=0.25]{fig2.png}
+\includegraphics[scale=0.15]{fig2.png}
 \caption{

### 2015-03-04 publishing/latex/figures.tex
updated figure 2

@@
 \caption{
-{\bf Oxygen Characterization.}  Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device.
-Each 6 well row of the plate can be controlled independently.
+{\bf Oxygen Characterization.} 
+(A) Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device.
+Error bars are the standard deviation N=3.
+(B) Four oxygen conditions are demonstrated in a 24-well plate.
+Each 6-well row of the plate can be controlled independently.  
 }

### 2015-03-06 publishing/latex/plos_template.tex
working on disscussion

@@
 
+This device provides convient oxygen control within a standard culture format.
+This device adds oxygen control will still allowing standard assays and imageing to occur, with the additon of a source of the gas of interest.
+3D-printing allows this design to be shared directly and modified by and end user without learning any microfabrication techniques.
+
+The device is also resuable. Typical microfulidic chips for the control of oxygen conditions are single use due to biological material fouling the gas pereapilty. 
+Due the the addheasive aplication of the membranes the have be easily removed and replaced with fresh ones allowing the device to be reused. 
+It is also convienat that the cell are not grow in the device.
+
 More mRNA stuff for megan to expand
@@
 Future directions: more channel networks, higher format plates, stackable plates with gas connections
+With the 3D printhing higher levels of intrececy can be achieved without complating fabrication.
+This allows any number of addtional features to be added.
+An on device mixer that could supply different levels of mixing between two sources of gas could reduce the number of tanks required.
+A mixer could also allow more conditions in a single plate perhaps even 1 per well or even gradients within wells.
+Even hight format plates such as 96 well plates could be used.
+Gas connections could be reloated to allow stacking of device in incubators.
 

### 2015-03-06 publishing/latex/plos_template.tex
working on dicussin

@@
 
-The 24 well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor as shown in Figure \ref{oxygen-char-figure}.
+\subsection*{Oxygen Control}
+The 24 well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor placed at the bottom of the well, as shown in Figure \ref{figure1}.
 Oxygen control was able to be controlled in each of the 6 wells equally from one gas input demonstrating the distribution network worked effectively.
 The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% \ce{O2} indefinitely, while 95\% \ce{N2}, 5\% \ce{CO2} is pumped through the device. 
-A different gas condition can be used in each sepereate iteration of the 6-well unit allowing 6 tecnical replicants of up to 4 different gas conditions in one 24 well plate\ref{fig2}.
+A different gas condition can be used in each sepereate iteration of the 6-well unit allowing 6 tecnical replicants of up to 4 different gas conditions in one 24 well plate\ref{figure2}.
 
+\subsection*{Bioverifcation}
 Bioverification of the devices ablility to control the gas enviroment is demonstrated with hypoxia influenced expression of mRNA in cancer cells\ref{fig3}.
+Oxygen levels of 21, 10, 5, and 0\% are applied to each set of 6 wells.
+
+More mRNA stuff for megan to expand \ref{figure3}
 
@@
 It is also convienat that the cell are not grow in the device.
-
-More mRNA stuff for megan to expand
 

### 2015-03-06 publishing/latex/plos_template.tex
working on discussion

@@
 
-This device provides convient oxygen control within a standard culture format.
-This device adds oxygen control will still allowing standard assays and imageing to occur, with the additon of a source of the gas of interest.
+This device provides convenient oxygen control within a standard culture format.
+This device adds oxygen control will still allowing standard assays and imaging to occur, with the addition of a source of the gas of interest.
 3D-printing allows this design to be shared directly and modified by and end user without learning any microfabrication techniques.
 
-The device is also resuable. Typical microfulidic chips for the control of oxygen conditions are single use due to biological material fouling the gas pereapilty. 
-Due the the addheasive aplication of the membranes the have be easily removed and replaced with fresh ones allowing the device to be reused. 
-It is also convienat that the cell are not grow in the device.
+The device is also reusable. Typical PDMS microfluidic chips for the control of oxygen conditions are single use due to biological material fouling the membrane gas permeability. 
+Due the the non-permanent application, the membranes can be easily pealed off and replaced with fresh ones allowing the device to be reused.
 
-Future directions: more channel networks, higher format plates, stackable plates with gas connections
-With the 3D printhing higher levels of intrececy can be achieved without complating fabrication.
-This allows any number of addtional features to be added.
+Moving forward with additive manufacturing of microfluidic devices is desirable. 
+3D printing higher levels of intricacy can be achieved without further complicating fabrication.
+This allows any number of additional features to be added.
 An on device mixer that could supply different levels of mixing between two sources of gas could reduce the number of tanks required.

### 2015-03-09 publishing/latex/plos_template.tex
working on discussion

@@
 \subsection*{Oxygen Control}
-The 24 well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor placed at the bottom of the well, as shown in Figure \ref{figure1}.
-Oxygen control was able to be controlled in each of the 6 wells equally from one gas input demonstrating the distribution network worked effectively.
+Oxygen control in the 24-well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor placed at the bottom of the well, as shown in Figure \ref{figure1}.
+Oxygen was able to be controlled in each of the 6 wells equally from one gas input demonstrating the distribution network worked effectively.
 The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% \ce{O2} indefinitely, while 95\% \ce{N2}, 5\% \ce{CO2} is pumped through the device. 
@@
 \subsection*{Bioverifcation}
-Bioverification of the devices ablility to control the gas enviroment is demonstrated with hypoxia influenced expression of mRNA in cancer cells\ref{fig3}.
+The devices ablility to control the gas enviroment is demonstrated with hypoxia influenced expression of mRNA in cancer cells\ref{fig3}.
 Oxygen levels of 21, 10, 5, and 0\% are applied to each set of 6 wells.
@@
 
-This device provides convenient oxygen control within a standard culture format.
-This device adds oxygen control will still allowing standard assays and imaging to occur, with the addition of a source of the gas of interest.
-3D-printing allows this design to be shared directly and modified by and end user without learning any microfabrication techniques.
+This new iteration of the multi-well insert for oxygen control maintains the convient features of the previous design.
+Oxygen contol is preformed in an off-the-shelf culture plate allowing standard protocols to be used for analysis assays or imaging where additional protocols are often requried when cells are seeded within microfuildic chips.
 
-The device is also reusable. Typical PDMS microfluidic chips for the control of oxygen conditions are single use due to biological material fouling the membrane gas permeability. 
-Due the the non-permanent application, the membranes can be easily pealed off and replaced with fresh ones allowing the device to be reused.
+This 3D-printed device improves on our previous design in a number of ways.
+First, the fabrication is greatly simplified. 
+No microfabrication, PDMS molding or Parylene coating is required.
+3D-printing also enables higher levels of intricacy without any additional fabrication allowing us to include the distribution network and the pipe within a pipe design. 
+Moving forward with additive manufacturing of microfluidic devices is desirable. 
+A comprable PDMS device would require several additional microfabriated layers to be manually aligned to reporduce just the distribution newtork.
+Additionally, the non-premanat addheasion of membranes to the 3D-part allow them to be removed and replaced if they are damaged.
+In PDMS devices the layers are bonded permantly via plasma bonding so damage to a membrane is not repairable.
 
-Moving forward with additive manufacturing of microfluidic devices is desirable. 
-3D printing higher levels of intricacy can be achieved without further complicating fabrication.
-This allows any number of additional features to be added.
+3D-printing allows this design to be shared directly and modified by an end user without requireing any microfabrication techniques.
 An on device mixer that could supply different levels of mixing between two sources of gas could reduce the number of tanks required.

### 2015-03-10 publishing/latex/plos_template.tex
working on discussion

@@
 No microfabrication, PDMS molding or Parylene coating is required.
-3D-printing also enables higher levels of intricacy without any additional fabrication allowing us to include the distribution network and the pipe within a pipe design. 
+3D-printing also enables higher levels of intricacy without any additional fabrication allowing us to include the distribution network and the 'pipe within a pipe' design. 
 Moving forward with additive manufacturing of microfluidic devices is desirable. 

### 2015-03-10 publishing/latex/plos_template.tex
fixed discussion and spell checked

@@
 The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% \ce{O2} indefinitely, while 95\% \ce{N2}, 5\% \ce{CO2} is pumped through the device. 
-A different gas condition can be used in each sepereate iteration of the 6-well unit allowing 6 tecnical replicants of up to 4 different gas conditions in one 24 well plate\ref{figure2}.
+A different gas condition can be used in each separate iteration of the 6-well unit allowing 6 technical replicates of up to 4 different gas conditions in one 24 well plate\ref{figure2}.
 
 \subsection*{Bioverifcation}
-The devices ablility to control the gas enviroment is demonstrated with hypoxia influenced expression of mRNA in cancer cells\ref{fig3}.
+The devices ability to control the gas environment is demonstrated with hypoxia influenced expression of mRNA in cancer cells\ref{fig3}.
 Oxygen levels of 21, 10, 5, and 0\% are applied to each set of 6 wells.
 
-More mRNA stuff for megan to expand \ref{figure3}
+More mRNA stuff for Megan to expand \ref{figure3}
 
-This new iteration of the multi-well insert for oxygen control maintains the convient features of the previous design.
-Oxygen contol is preformed in an off-the-shelf culture plate allowing standard protocols to be used for analysis assays or imaging where additional protocols are often requried when cells are seeded within microfuildic chips.
+This new iteration of the multi-well insert for oxygen control maintains the convenient features of the previous design.
+Oxygen control is preformed in an off-the-shelf culture plate allowing standard protocols to be used for analysis assays or imaging where additional protocols are often required when cells are seeded within microfluidic chips.
 
@@
 No microfabrication, PDMS molding or Parylene coating is required.
+Additionally, the non-permanent adhesion of membranes to the 3D-part allow them to be removed and replaced if they are damaged.
+In PDMS devices the layers are bonded permanently via plasma bonding so damage to a membrane is not repairable.
 3D-printing also enables higher levels of intricacy without any additional fabrication allowing us to include the distribution network and the 'pipe within a pipe' design. 
-Moving forward with additive manufacturing of microfluidic devices is desirable. 
-A comprable PDMS device would require several additional microfabriated layers to be manually aligned to reporduce just the distribution newtork.
-Additionally, the non-premanat addheasion of membranes to the 3D-part allow them to be removed and replaced if they are damaged.
-In PDMS devices the layers are bonded permantly via plasma bonding so damage to a membrane is not repairable.
+A comparable PDMS device would require several additional microfabricated layers to be manually aligned to reproduce just the distribution network.
 
-3D-printing allows this design to be shared directly and modified by an end user without requireing any microfabrication techniques.
-An on device mixer that could supply different levels of mixing between two sources of gas could reduce the number of tanks required.
-A mixer could also allow more conditions in a single plate perhaps even 1 per well or even gradients within wells.
-Even hight format plates such as 96 well plates could be used.
-Gas connections could be reloated to allow stacking of device in incubators.
+Moving forward with additive manufacturing of microfluidic devices is desirable as it will enable highly integrated designs without any additional fabrication.
+For this device an on-device gas mixer could allow more conditions in a single plate, perhaps even one per well or even gradients within wells while reducing the number of gas tanks required.
+This design could also be applied to higher format plates such as 96-well plates.
 

### 2015-03-11 publishing/latex/plos_template.tex
added figure 3 and spellchecked

@@
 This expands on our previous work of a similar device for 6-well plates\cite{Oppegard2009,Oppegard2010}.
-The ability to independentaly control oxygen across each row of the plate enables more efficient experiments as a separate incubator or hypoxic chamber is not needed for each condition.
+The ability to independently control oxygen across each row of the plate enables more efficient experiments as a separate incubator or hypoxic chamber is not needed for each condition.
 
@@
 Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Shallan 2014, Chen2014, Erkal2014,Bhargava2014}. 
-Many prototypical microfluidic device features have been recreated with 3D printing as a proof of concept for this new fabrication technique \cite{Au2014, Shallan2014} including modular re-configurable units\cite{Bharagava2014}.
+Many prototypical microfluidic device features have been recreated with 3D printing as a proof of concept for this new fabrication technique \cite{Au2014, Shallan2014} including modular re-configurable units\cite{Bhargava2014}.
 3D printed devices have been used for inexpensive and high-throughput reactionware,\cite{Kitson2014}, for a measuring dopamine and ATP levels in biological samples with an integrated electrode\cite{Erkal2014}, as well as a device that allows flow through measurements of ATP to be taken with a plate reader\cite{Chen2014}.
@@
 In this case, having a gas-impermeable material for the bulk is advantageous as it reduces unwanted gas transfer. 
-The previous PDMS devices were parylene coated along the convection channels to eliminate exchange of gas from the PDMS bulk, which again added to their complexity and is now longer needed.
+The previous PDMS devices were Parylene coated along the convection channels to eliminate exchange of gas from the PDMS bulk, which again added to their complexity and is now longer needed.
 Convection and distribution of the gas is done in the impermeable material eliminating dilution of the gas before reaching the diffusion layer.
@@
 The device was designed to integrate with a multiwell format, specifically an off-the-shelf 24 well plate. 
-The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{oppegard2010} and also incorporates an integrated distribution network and hose barbs to simplify device operation.
+The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{Oppegard2010} and also incorporates an integrated distribution network and hose barbs to simplify device operation.
 The pillars extend into each well leaving a $\sim$500 $\mu$m gap for media between the diffusion membrane and the culture surface at the bottom of the well.
 Diffusion occurs rapidly across this gap allowing control of the dissolved gas environment around the cells. 
-A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells (Figure \ref{figure1}.
+A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells (Figure \ref{figure1}).
 
-The device also features a pipe within a pipe design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Figure \ref{figure1}.
+The device also features a pipe within a pipe design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Figure \ref{figure1}).
 Again the membranes are adhered with a thin layer of PDMS on the membrane and allowed to cure in place.
@@
 Oxygen was measured with PtOEPK (Pt(II) Octaethylporphine ketone) planar sensors that were fixed to the bottom of a 24 well plate. 
-The intensity of the sensor was measured and correlated to the concentration of oxygen with Stern-Volmer analysis (Figure \ref{piller-well-render-figure}.
+The intensity of the sensor was measured and correlated to the concentration of oxygen with Stern-Volmer analysis (Figure \ref{figure1}).
 Gas was perfused through the device with negative pressure to reduce membrane debonding and was also found to reduce the number of bubbles formed in the culture chamber.
@@
 All gas tanks used in the oxygen characterization were 5\% CO2 in addition to the desired gas mix in anticipation of cell culture experiments as CO2 can alter the fluorescence of the PtOEPK.
-Intensity measurments were taken every five minutes for each well.
-Initially the inlets are fed with a 5\% \ce{CO2}, bal. air tank until the intensity stableized.
-The inlets are then switched to the contol gas of either 0, 5 10 or 21\% \ce{O2}, each with 5\% \ce{CO2} and balanced with \ce{N2}.
+Intensity measurements were taken every five minutes for each well.
+Initially the inlets are fed with a 5\% \ce{CO2}, bal. air tank until the intensity stabilized.
+The inlets are then switched to the control gas of either 0, 5 10 or 21\% \ce{O2}, each with 5\% \ce{CO2} and balanced with \ce{N2}.
 Intensity measurements are then taken every five minutes for six hours.
-The this entire procedure was reapeated three times for and N of three.
+The this entire procedure was repeated three times for and N of three.
 
@@
 Cancer cells were seeded in a 24 well plate.
-When they reached $\sim$70\% confluency the 24-well insert is placed in the plate and the gasses are perfused through the device in the same scheme as in the oxygen characterization.
+When they reached $\sim$70\% confluency the 24-well insert is placed in the plate and the gases are perfused through the device in the same scheme as in the oxygen characterization.
 Each row of six wells experiences either 0, 5, 10 or 21\% \ce{O2}, with 5\% \ce{CO2} and balanced nitrogen.
-The assmebly is placed in an incubator at $37\,^{\circ}\mathrm{C}$ for six hours.
+The assembly is placed in an incubator at $37\,^{\circ}\mathrm{C}$ for six hours.
 
@@
 The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% \ce{O2} indefinitely, while 95\% \ce{N2}, 5\% \ce{CO2} is pumped through the device. 
-A different gas condition can be used in each separate iteration of the 6-well unit allowing 6 technical replicates of up to 4 different gas conditions in one 24 well plate\ref{figure2}.
+A different gas condition can be used in each separate iteration of the 6-well unit allowing 6 technical replicates of up to 4 different gas conditions in one 24 well plate (Figure \ref{figure2}).
 
 \subsection*{Bioverifcation}
-The devices ability to control the gas environment is demonstrated with hypoxia influenced expression of mRNA in cancer cells\ref{fig3}.
+The devices ability to control the gas environment is demonstrated with hypoxia influenced expression of mRNA in cancer cells (Figure \ref{figure3}).
 Oxygen levels of 21, 10, 5, and 0\% are applied to each set of 6 wells.
 
-More mRNA stuff for Megan to expand \ref{figure3}
+More mRNA stuff for Megan to expand (Figure \ref{figure3}).
 
+\subsection*{Discussion}
 This new iteration of the multi-well insert for oxygen control maintains the convenient features of the previous design.
@@
 
-%\section*{References}
+\section*{References}
 
@@
 
-\begin{figure}
-%\includegraphics[scale=0.2]{../presentation-figures/piller-well-render-with-arrows.png} % remove for manuscript submission
+\begin{figure}[H]
 \caption{
-{\bf CAD rendering of the piller bottom.} The 'Pipe with in a pipe' flow pattern delivers gas to the bottom of each well where it diffuses to the culture.  
+{\bf Design of 24-well Insert Device.}
+(A) Rendering of whole 3D printed part.
+An inlet and outlet barb allows perfusion of gas to control 6 channels.
+(B) At the bottom of each pillar gas entering from the outer channel flows along the PDMS membrane (blue), which is supported by micropillars, and exhausts via the inner pipe.
+Diffusion occurs rapidly through the PDMS membrane to the cell culture spaced 500 $\mu$m away at the bottom of the well.
+(C) Cross-section demonstrating how the microfluidic distribution network and double pipes are connected. 
+The two adjacent mirrored distribution networks are spaced 1 mm apart along the z-axis allowing them to overlap and enter the separate vertical pipes.
+The arrows indicate the flow direction.
+The incoming gas enters enters the outer pipe on its way to the bottom of the well and returns through the inner pipe.
+(D) Photo of the device with dyed channels in a 24-well plate.
+(E) Photo of the device from the bottom with four independent channel networks.
+(F) Photo of the printed distribution networks.
 }
-\label{piller-well-render-figure}
+\label{figure1}
 \end{figure}
 
-\begin{figure}
-%\includegraphics[scale=0.05]{../presentation-figures/24well.JPG} % remove for manuscript submission
-%\includegraphics[scale=0.05]{../presentation-figures/printed-network.JPG} % remove for manuscript submission
+\begin{figure}[H]
 \caption{
-{\bf Photographs of the printed device.}  The printed device with membranes adhered. The distribution network is printed completely in resin.
+{\bf Oxygen Characterization.} 
+(A) Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device.
+Error bars are the standard deviation N=3.
+(B) Four oxygen conditions are demonstrated in a 24-well plate.
+Each 6-well row of the plate can be controlled independently.  
+Mean N=3 error bars not included.
 }
-\label{device-photos-figure}
+\label{figure2}
 \end{figure}
 
-\begin{figure}
-%\includegraphics[scale=0.3]{../presentation-figures/6-well-plot.png} % remove for manuscript submission
-%\includegraphics[scale=0.3]{../presentation-figures/24-well-plot.png} % remove for manuscript submission
+\begin{figure}[H]
+%\includegraphics[scale=0.2]{image.jpg} % remove for manuscript submission
 \caption{
-{\bf Oxygen Characterization.}  Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device.
-Each 6 well row of the plate can be controlled independently.
+{\bf PCR Data.}  VEGF expression in A549 cells after exposure to different oxygen conditions.
 }
-\label{oxygen-char-figure}
+\label{figure3}
 \end{figure}
 
-\begin{figure}
-%\includegraphics[scale=0.2]{image.jpg} % remove for manuscript submission
-\caption{
-{\bf PCR Data.}  Not finished yet.  
-}
-\label{pcr-data}
-\end{figure}
-
-\section*{Tables}
+%\section*{Tables}
 % 
@@
 
-\section*{Supporting Information Legends}
+%\section*{Supporting Information Legends}
 %

### 2015-03-20 publishing/latex/paper.tex
converted to new template, added paper.tex to be used as main

--- 2015-03-11 publishing/latex/plos_template.tex
@@
 % Template for PLoS
-% Version 2.0 July 2014
+% Version 3.1 February 2015
 %
@@
 %
-% Be advised that this is merely a template 
-% designed to facilitate accurate translation of manuscript content 
-% into our production files. 
-%
-% This template contains extensive comments intended 
+% This template contains comments intended 
 % to minimize problems and delays during our production 
-% process. Please follow the template 
+% process. Please follow the template instructions
 % whenever possible.
@@
 %
-% Once your paper is accepted for publication and enters production, 
+% Once your paper is accepted for publication, 
 % PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
@@
 %
-% DO NOT ADD EXTRA PACKAGES TO THIS TEMPLATE unless absolutely necessary.
-% Packages included in this template are intentionally
-% limited and basic in order to reduce the possibility
-% of issues during our production process.
+% There are no restrictions on package use within the LaTeX files except that 
+% no packages listed in the template may be deleted.
+%
+% Please do not include colors or graphics in the text.
+%
+% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
 %
@@
 %
+% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
+%
 % DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
@@
 % - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% For figure citations, please use "Fig." instead of "Figure".
 % See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
@@
 % Tables should be cell-based and may not contain:
-% - tabs/spacing/line breaks within cells to alter layout
+% - tabs/spacing/line breaks within cells to alter layout or alignment
 % - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
@@
 %
-% For sideways tables, use the {rotating} package and use \begin{sidewaystable} instead of \begin{table} in the appropriate section. PLOS guidelines do not accomodate sideways figures.
+% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
 %
@@
 %
-% Please be sure to include all portions of an equation in the math environment, and for any superscripts or subscripts also include the base number/text.
-For example, use $mathrm{mm}^2$ instead of mm$^2$ (do not use \textsuperscript command).
+% Please be sure to include all portions of an equation in the math environment.
 %
-% DO NOT USE the \rm command to render mathmode characters in roman font, instead use $\mathrm{}$
-% For bolding characters in mathmode, please use $\mathbf{}$ 
+% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
 %
-% Please add line breaks to long equations when possible in order to fit our 2-column layout. 
+% Please add line breaks to long display equations when possible in order to fit size of the column. 
 %
-% For inline equations, please do not include punctuation within the math environment unless this is part of the equation.
+% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
 %
-% For spaces within the math environment please use the \; or \: commands, even within \text{} (do not use smaller spacing as this does not convert well).
+% % % % % % % % % % % % % % % % % % % % % % % % 
 %
+% Please contact latex@plos.org with any questions.
 %
@@
 
-\documentclass[10pt]{article}
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
 
-% amsmath package, useful for mathematical formulas
-\usepackage{amsmath}
-% amssymb package, useful for mathematical symbols
-\usepackage{amssymb}
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% Use Unicode characters when possible
+\usepackage[utf8]{inputenc}
+
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% fixltx2e package for \textsubscript
+\usepackage{fixltx2e}
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
+\usepackage[version=3]{mhchem}  % added by author
 
@@
 
-\usepackage{hyperref}
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
 
 % line numbers
-\usepackage{lineno}
+\usepackage[right]{lineno}
 
@@
 % rotating package for sideways tables
-%\usepackage{rotating}
+\usepackage{rotating}
 
-% If you wish to include algorithms, please use one of the packages below.
-Also, please see the algorithm section of our LaTeX guidelines (http://www.plosone.org/static/latexGuidelines) for important information about required formatting.
-%\usepackage{algorithmic}
-%\usepackage{algorithmicx}
-
-% Use doublespacing - comment out for single spacing
+% Remove comment for double spacing
 %\usepackage{setspace} 
@@
 
-\usepackage[version=3]{mhchem}
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in 
+\textheight 8.75in
 
-% Text layout
-\topmargin 0.0cm
-\oddsidemargin 0.5cm
-\evensidemargin 0.5cm
-\textwidth 16cm 
-\textheight 21cm
-
-% Bold the 'Figure #' in the caption and separate it with a period
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
 % Captions will be left justified
-\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
 
 % Use the PLoS provided BiBTeX style
-\bibliographystyle{plos2009}
+\bibliographystyle{plos2015}
 
@@
 
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
 \pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\sf PLOS}
 
-%% Include all macros below. Please limit the use of macros.
+%% Include all macros below
+
+\newcommand{\lorem}{{\bf LOREM}}
+\newcommand{\ipsum}{{\bf IPSUM}}
 
@@
 \begin{document}
+\vspace*{0.35in}
 
-% Title must be 150 characters or less
+% Title must be 250 characters or less.
+% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
 \begin{flushleft}
 {\Large
-\textbf{3D-Printed Microfluidic Oxygen Control Devices}
+\textbf\newline{3D-Printed Microfluidic Oxygen Control Devices - Submission to PLOS ONE}
 }
-% Insert Author names, affiliations and corresponding author email.
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
 \\
-Martin D. Brennan$^{1}$, 
-Megan L. Rexius-Hall$^{1}$, 
-David T. Eddington$^{1,\ast}$
+Martin D. Brennan\textsuperscript{1},
+Megan L. Rexius-Hall\textsuperscript{1},
+David T. Eddington\textsuperscript{1,*},
 \\
+\bigskip
 \bf{1} Dept of Bioengineering, University of Illinois at Chicago, Chicago, Illinois, USA
 \\
-%\bf{2} Author2 Dept/Program/Center, Institution Name, City, State, Country
-%\\
-%\bf{3} Author3 Dept/Program/Center, Institution Name, City, State, Country
-%\\
-$\ast$ E-mail: Corresponding dte@uic.edu
+\bigskip
+
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+* dte@uic.edu
+
 \end{flushleft}
-
-% Please keep the abstract between 250 and 300 words
+% Please keep the abstract below 300 words
 \section*{Abstract}
-
 Recently 3D printing has emerged as a method for directly printing complete microfluidic chips, 
@@
 This is the first 3D printed device that can be functionalized to control oxygen in cell culture.
-%Two devices are presented and characterized.
 
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-\section*{Author Summary}
+\linenumbers
 
 \section*{Introduction}
-
 Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
@@
 \section*{Materials and Methods}
-
 \subsection*{Design of Insert}
@@
 Diffusion occurs rapidly across this gap allowing control of the dissolved gas environment around the cells. 
-A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells (Figure \ref{figure1}).
+A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells (Fig.~\ref{fig1}).
 
-The device also features a pipe within a pipe design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Figure \ref{figure1}).
+The device also features a pipe within a pipe design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Fig.~\ref{fig1}).
 Again the membranes are adhered with a thin layer of PDMS on the membrane and allowed to cure in place.
@@
 
+\begin{figure}[h]
+\caption{
+{\bf Design of 24-well Insert Device.}
+(A) Rendering of whole 3D printed part.
+An inlet and outlet barb allows perfusion of gas to control 6 channels.
+(B) At the bottom of each pillar gas entering from the outer channel flows along the PDMS membrane (blue), which is supported by micropillars, and exhausts via the inner pipe.
+Diffusion occurs rapidly through the PDMS membrane to the cell culture spaced 500 $\mu$m away at the bottom of the well.
+(C) Cross-section demonstrating how the microfluidic distribution network and double pipes are connected. 
+The two adjacent mirrored distribution networks are spaced 1 mm apart along the z-axis allowing them to overlap and enter the separate vertical pipes.
+The arrows indicate the flow direction.
+The incoming gas enters enters the outer pipe on its way to the bottom of the well and returns through the inner pipe.
+(D) Photo of the device with dyed channels in a 24-well plate.
+(E) Photo of the device from the bottom with four independent channel networks.
+(F) Photo of the printed distribution networks.
+}
+\label{fig1}
+\end{figure}
+
 \subsection*{Oxygen characterization}
@@
 Oxygen was measured with PtOEPK (Pt(II) Octaethylporphine ketone) planar sensors that were fixed to the bottom of a 24 well plate. 
-The intensity of the sensor was measured and correlated to the concentration of oxygen with Stern-Volmer analysis (Figure \ref{figure1}).
+The intensity of the sensor was measured and correlated to the concentration of oxygen with Stern-Volmer analysis (Fig.~\ref{fig2}).
 Gas was perfused through the device with negative pressure to reduce membrane debonding and was also found to reduce the number of bubbles formed in the culture chamber.
@@
 
+\begin{figure}[h]
+\caption{
+{\bf Oxygen Characterization.} 
+(A) Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device.
+Error bars are the standard deviation N=3.
+(B) Four oxygen conditions are demonstrated in a 24-well plate.
+Each 6-well row of the plate can be controlled independently.  
+Mean N=3 error bars not included.
+}
+\label{fig2}
+\end{figure}
+
 \subsection*{Cell culture and hypoxia assay}
@@
 Each row of six wells experiences either 0, 5, 10 or 21\% \ce{O2}, with 5\% \ce{CO2} and balanced nitrogen.
-The assembly is placed in an incubator at $37\,^{\circ}\mathrm{C}$ for six hours.
+The assembly is placed in an incubator at $37\,^{\circ}\mathrm{C}$ for six hours (Fig.~\ref{fig3}).
+
+\begin{figure}[h]
+\caption{
+{\bf PCR Data.}  VEGF expression in A549 cells after exposure to different oxygen conditions.
+}
+\label{fig3}
+\end{figure}
+
+% For figure citations, please use "Fig." instead of "Figure".
+%Nulla mi mi, Fig.~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam.
+Proin rutrum vel massa non gravida.
+Quisque tempor sem et dignissim rutrum.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Morbi at justo vitae nulla elementum commodo eu id massa.
+In vitae diam ac augue semper tincidunt eu ut eros.
+Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis.
+Aliquam in enim semper, aliquam massa id, cursus neque.
+Praesent faucibus semper libero.
+
+%\begin{enumerate}
+%\item{react}
+%\item{diffuse free particles}
+%\item{increment time by dt and go to 1}
+%\end{enumerate}
 
 % Results and Discussion can be combined.
-\section*{Results and Discussion}
-
+\section*{Results}
 \subsection*{Oxygen Control}
-Oxygen control in the 24-well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor placed at the bottom of the well, as shown in Figure \ref{figure1}.
+Oxygen control in the 24-well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor placed at the bottom of the well, as shown in Fig.~\ref{fig2}.
 Oxygen was able to be controlled in each of the 6 wells equally from one gas input demonstrating the distribution network worked effectively.
 The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% \ce{O2} indefinitely, while 95\% \ce{N2}, 5\% \ce{CO2} is pumped through the device. 
-A different gas condition can be used in each separate iteration of the 6-well unit allowing 6 technical replicates of up to 4 different gas conditions in one 24 well plate (Figure \ref{figure2}).
+A different gas condition can be used in each separate iteration of the 6-well unit allowing 6 technical replicates of up to 4 different gas conditions in one 24 well plate (Fig.~\ref{fig2}).
 
 \subsection*{Bioverifcation}
-The devices ability to control the gas environment is demonstrated with hypoxia influenced expression of mRNA in cancer cells (Figure \ref{figure3}).
+The devices ability to control the gas environment is demonstrated with hypoxia influenced expression of mRNA in cancer cells (Fig.~\ref{fig3}).
 Oxygen levels of 21, 10, 5, and 0\% are applied to each set of 6 wells.
 
-More mRNA stuff for Megan to expand (Figure \ref{figure3}).
+More mRNA stuff for Megan to expand (Fig.~\ref{fig3}).
 
@@
 
-% We only support three levels of headings, please do not create a heading level below \subsubsection.
-\subsection*{Subsection 1}
+%\begin{table}[!ht]
+%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+%\caption{
+%{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
+%\begin{tabular}{|l|l|l|l|l|l|l|l|}
+%\hline
+%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
+%$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ %\hline
+%$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ %\hline
+%$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ %\hline
+%\end{tabular}
+%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec %pellentesque metus tortor nec nisl.
+Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
+%\end{flushleft}
+%\label{table1}
+%\end{adjustwidth}
+%\end{table}
 
-\subsubsection*{SubSubsection 1.1}
+% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}. 
+For more information, see \nameref{S1_Text}.
 
-\subsection*{Subsection 2}
+%\section*{Supporting Information}
 
-%\section*{Discussion}
+% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
+%\subsection*{S1 Video}
+%\label{S1_Video}
+%{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+%Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur %pellentesque.
 
-\section*{Conclusion}
-3D printing microfluidic chips have been limited to non oxygen permeable materials.
-We demonstrate oxygen control in 3D printed devices the addition of a gas permeable PDMS membrane. 
-Oxygen control is demonstrated in a 24 well plate and PCR analysis of X in Y cells shows the device effectively controls oxygen as expected.
-3D printing allows complex designs, integrated tubing connectors, and is comparable in price to standard PDMS fabrication.
-This technique represents a bridge to commercialization where robust devices can be more easily shared and disseminated.
-While injection molding, hot embossing, or other industrial processes are cheaper when making hundreds to thousands of devices, it is not practical to make a injection mold when making tens to hundreds of devices.
-In addition, PDMS fabrication would be too time consuming, expensive, and the failure rate would be unacceptable.
-3D printing is a perfect solution to these device fabrication needs.
+%\subsection*{S1 Text}
+%\label{S1_Text}
+%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac %ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur %pellentesque.
 
-% Do NOT remove this, even if you are not including acknowledgments.
+%\subsection*{S1 Fig}
+%\label{S1_Fig}
+%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac %ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur %pellentesque.
+
+%\subsection*{S2 Fig}
+%\label{S2_Fig}
+%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac %ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur %pellentesque.
+
+%\subsection*{S1 Table}
+%\label{S1_Table}
+%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac %ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur %pellentesque.
 
 \section*{Acknowledgments}
-
 This work funded by NSF 1253060.
 
+\nolinenumbers
+
 \section*{References}
-
+\bibliographystyle{plos2015.bst}
 \bibliography{references}
 
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% OR
-%
-% Compile your BiBTeX database using our plos2009.bst
-% style file and paste the contents of your .bbl file
-% here.
-%
-
-\section*{Figure Legends}
-% This section is for figure legends only, do not include
-% graphics in your manuscript file.
-%
-%\begin{figure}
-%\caption{
-%{\bf Bold the first sentence.}  Rest of figure caption.  
-%}
-%\label{Figure_label}
-%\end{figure}
-
-% copy and paste for figures
-%\begin{figure}
-%\includegraphics[scale=0.2]{image.jpg} % remove for manuscript submission
-%\caption{
-%{\bf Bold the first sentence.}  Rest of figure caption.  
-%}
-%\label{Figure_label}
-%\end{figure}
-
-\begin{figure}[H]
-\caption{
-{\bf Design of 24-well Insert Device.}
-(A) Rendering of whole 3D printed part.
-An inlet and outlet barb allows perfusion of gas to control 6 channels.
-(B) At the bottom of each pillar gas entering from the outer channel flows along the PDMS membrane (blue), which is supported by micropillars, and exhausts via the inner pipe.
-Diffusion occurs rapidly through the PDMS membrane to the cell culture spaced 500 $\mu$m away at the bottom of the well.
-(C) Cross-section demonstrating how the microfluidic distribution network and double pipes are connected. 
-The two adjacent mirrored distribution networks are spaced 1 mm apart along the z-axis allowing them to overlap and enter the separate vertical pipes.
-The arrows indicate the flow direction.
-The incoming gas enters enters the outer pipe on its way to the bottom of the well and returns through the inner pipe.
-(D) Photo of the device with dyed channels in a 24-well plate.
-(E) Photo of the device from the bottom with four independent channel networks.
-(F) Photo of the printed distribution networks.
-}
-\label{figure1}
-\end{figure}
-
-\begin{figure}[H]
-\caption{
-{\bf Oxygen Characterization.} 
-(A) Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device.
-Error bars are the standard deviation N=3.
-(B) Four oxygen conditions are demonstrated in a 24-well plate.
-Each 6-well row of the plate can be controlled independently.  
-Mean N=3 error bars not included.
-}
-\label{figure2}
-\end{figure}
-
-\begin{figure}[H]
-%\includegraphics[scale=0.2]{image.jpg} % remove for manuscript submission
-\caption{
-{\bf PCR Data.}  VEGF expression in A549 cells after exposure to different oxygen conditions.
-}
-\label{figure3}
-\end{figure}
-
-%\section*{Tables}
-% 
-% See introductory notes if you wish to include sideways tables.
-%
-% NOTE: Please look over our table guidelines at http://www.plosone.org/static/figureGuidelines#tables to make sure that your tables meet our requirements.
-Certain types of spacing, cell merging, and other formatting tricks may have unintended results and will be returned for revision.
-%
-%\begin{table}[!ht]
-%\caption{
-%\bf{Table title}}
-%\begin{tabular}{|c|c|c|}
-%table information
-%\end{tabular}
-%\begin{flushleft}Table caption
-%\end{flushleft}
-%\label{tab:label}
-% \end{table}
-
-%\section*{Supporting Information Legends}
-%
-% Please enter your Supporting Information captions below in the following format:
-%\item{\bf Figure SX. Enter mandatory title here.} Enter optional descriptive information here.
-% 
-%\begin{description}
-%\item {\bf}
-%\item {\bf}
-%\end{description}
-
 \end{document}

### 2015-03-27 publishing/latex/paper.tex
working on intro, added many new citations

@@
 Dissemination and distributed production is also vastly simplified due to easy sharing of the design as a CAD file.
-Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Shallan 2014, Chen2014, Erkal2014,Bhargava2014}. 
-Many prototypical microfluidic device features have been recreated with 3D printing as a proof of concept for this new fabrication technique \cite{Au2014, Shallan2014} including modular re-configurable units\cite{Bhargava2014}.
-3D printed devices have been used for inexpensive and high-throughput reactionware,\cite{Kitson2014}, for a measuring dopamine and ATP levels in biological samples with an integrated electrode\cite{Erkal2014}, as well as a device that allows flow through measurements of ATP to be taken with a plate reader\cite{Chen2014}.
+Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014,Comina2014, Chen2014,Shallan2014,Bhargava2014}. 
+Many prototypical microfluidic device features have been recreated with 3D printing as a proof of concept for this new fabrication technique \cite{ Au2014, Shallan2014} including modular re-configurable units\cite{Yuen2008,Bhargava2014,Lee2014}.
+3D printed devices have been used for neuroengineering applications\cite{Tek2008}, inexpensive and high-throughput reactionware,\cite{Kitson2012,Symes2012, Kitson2014}, culturing and imaging arrays of seedlings\cite{Busch2012}, measuring dopamine and ATP levels in biological samples with an integrated electrode\cite{Erkal2014}, or plate reader\cite{Chen2014}, and a bacteria separation flow assay\cite{Lee2014a,Lee2015}.
+Other 3D printed fluidic devices include pneumatic valves\cite{Au2015} a custom NMR cell\cite{Causier2015}, a rapid reconstitution package for lyophilized drugs\cite{Chi2014} and flow plates for a water electrolysis system\cite{Chisholm2014}.
 
 Printing is currently limited in choice of materials compatible with the process and include many proprietary formulations, regardless these have been successfully used in a variety of applications.
+New techniques for using a 3D printed molds to produce devices\cite{Mcdonald2002,King2014,Comina2014a,Gregory2013} are also being developed, including fugitive ink methods\cite{Therriault2003,Miller2012,Bhargava2015}.
 As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials although this area is being developed\cite{Femmer2014}.
-Microfluidic cell culture devices are most commonly cast in PDMS.
-PDMS is a convenient material for cell studies due to it's biocompatibility, optical properties, and gas permeability, facilitating oxygen control of cell environments.
+Microfluidic cell culture devices are most commonly cast in PDMS as it is a convenient material for cell studies due to it's biocompatibility, optical properties, and gas permeability, facilitating oxygen control of cell environments\cite{Sia2003,Brennan2014}.
 

### 2015-03-27 publishing/latex/paper.tex
update intro, re added conclusion

@@
 
-3D printing of microfluidic devices enables rapid, one-step fabrication of complex designs infeasible to make with planar lithography and replica molding techniques.
+3D printing of microfluidic devices enables rapid, one-step fabrication of complex designs infeasible to make with planar lithography and replica molding techniques\cite{Waldbaur2011,Chen2014a}.
 In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
 It is not unusual for microfluidic labs to make ten microfluidic devices to guarantee one will work properly.
-On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which may be outsourced to a 3D printing company for around \$100/device \cite{Au2014}.
+On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which may be outsourced to a 3D printing company for around \$200/device \cite{Au2014}.
 3D printing also allows integration of complex geometries not possible with planar lithography, such as hose barbs and luer fittings.
@@
 Printing is currently limited in choice of materials compatible with the process and include many proprietary formulations, regardless these have been successfully used in a variety of applications.
-New techniques for using a 3D printed molds to produce devices\cite{Mcdonald2002,King2014,Comina2014a,Gregory2013} are also being developed, including fugitive ink methods\cite{Therriault2003,Miller2012,Bhargava2015}.
-As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials although this area is being developed\cite{Femmer2014}.
+New techniques for using a 3D printed molds to produce devices\cite{Mcdonald2002,Gregory2013,King2014,Comina2014a} are also being developed, including fugitive ink methods\cite{Therriault2003,Miller2012,Bhargava2015}.
+As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials although this area is being developed\cite{Femmer2014a}.
 Microfluidic cell culture devices are most commonly cast in PDMS as it is a convenient material for cell studies due to it's biocompatibility, optical properties, and gas permeability, facilitating oxygen control of cell environments\cite{Sia2003,Brennan2014}.
@@
 Oxygen control in cells studies is often overlooked by researchers, but important for mimicking conditions experienced by cells in vivo.
-Typically cell culture studies are preformed at 21\% oxygen, atmospheric oxygen conditions, although levels that cells experience in vivo are usually less.
-For example tumors, in general, are hypoxic as they rapidly out grow their vasculature creating a hypoxic inner region. 
-To better study the role of oxygen levels in cancer gene expression a gas controlled culture system is required. ----I have to cite all this----
+Typically cell culture studies are preformed at 21\% oxygen, atmospheric oxygen conditions, although levels that cells experience in vivo are usually less\cite{Brennan2014}.
+For example tumors, in general, are hypoxic as they rapidly out grow their vasculature creating a hypoxic inner region\cite{Kumar2014}.
+To better study the role of oxygen levels in cancer gene expression a gas controlled culture system is required.
 
@@
 
+\section*{Conclusion}
+3D printing microfluidic chips have been limited to non oxygen permeable materials. We demonstrate oxygen control in 3D printed devices the addition of a gas permeable PDMS membrane. 
+Oxygen control is demonstrated in a 24 well plate and PCR analysis of X in Y cells shows the device effectively controls oxygen as expected. 
+3D printing allows complex designs, integrated tubing connectors, and is comparable in price to standard PDMS fabrication. 
+This technique represents a bridge to commercialization where robust devices can be more easily shared and disseminated. 
+While injection molding, hot embossing, or other industrial processes are cheaper when making hundreds to thousands of devices, it is not practical to make a injection mold when making tens to hundreds of devices.
+In addition, PDMS fabrication would be too time consuming, expensive, and the failure rate would be unacceptable. 3D printing is a perfect solution to these device fabrication needs.
+
 %\begin{table}[!ht]
@@
 % Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}. 
-For more information, see \nameref{S1_Text}.
+%For more information, see \nameref{S1_Text}.
 
@@
 
-\section*{References}
+%\section*{References}
 \bibliographystyle{plos2015.bst}

### 2015-04-12 publishing/latex/paper.tex
adding megans edits

@@
 \section*{Abstract}
-Recently 3D printing has emerged as a method for directly printing complete microfluidic chips, 
-although printing materials have been limited to non-oxygen permeable materials.
+Recently 3D printing has emerged as a method for directly printing complete microfluidic chips, although printing materials have been limited to non-oxygen permeable materials.
 We demonstrate the addition of gas permeable PDMS (Polydimethylsiloxane) membranes to 3D printed microfluidic devices as a means to enable oxygen control cell culture studies.
-This was demonstrated on an expanded 24 well version of our previous device which was for a 6-well plate.
+The incorporation of a 3D-printed device and gas-permeable membranes was demonstrated on an expanded 24-well version of our previous entirely PDMS device which was an insert for a 6-well plate.
 The direct printing allows integrated distribution channels and device geometries not possible with traditional planar lithography.
-With this device oxygen was able to be controlled to 4 different conditions across a 24 well plate demonstrating regulation of oxygen sensitive transcriptional protein in cancer cells.
-This is the first 3D printed device that can be functionalized to control oxygen in cell culture.
+With this device, four different oxygen conditions were able to be controlled and six wells were maintained under each oxygen condition. 
+We domonstrate enhanced transcrtiption of VEGFA (vascular endothelial growth factor A) gene with decreasing oxygen levels in human lung adenocarcinoma cells.
+This is the first 3D-printed device that can be functionalized to control oxygen in cell culture.
 
@@
 Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
-We demonstrate a device that nests into a 24 well culture plate to control gas in each row of the plate independently of the incubator's condition.
-This expands on our previous work of a similar device for 6-well plates\cite{Oppegard2009,Oppegard2010}.
+We demonstrate a device that nests into a 24-well culture plate to control gas in each row of the plate independently of the incubator's condition.
+This expands on our previous work of a device fabricated using PDMS molds and planar lithography for 6-well plates\cite{Oppegard2009,Oppegard2010}.
 The ability to independently control oxygen across each row of the plate enables more efficient experiments as a separate incubator or hypoxic chamber is not needed for each condition.
@@
 
-Printing is currently limited in choice of materials compatible with the process and include many proprietary formulations, regardless these have been successfully used in a variety of applications.
-New techniques for using a 3D printed molds to produce devices\cite{Mcdonald2002,Gregory2013,King2014,Comina2014a} are also being developed, including fugitive ink methods\cite{Therriault2003,Miller2012,Bhargava2015}.
-As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials although this area is being developed\cite{Femmer2014a}.
+Printing is currently limited in choice of substate compatible with the 3D printing process.
+Substrate options include many proprietary formulations which have been successfully used in a variety of applications.
+New techniques for using a 3D-printed molds to produce devices\cite{Mcdonald2002,Gregory2013,King2014,Comina2014a} are also being developed, including fugitive ink methods\cite{Therriault2003,Miller2012,Bhargava2015}.
+To date, there are no widely available methods or materials to facilitate direct printing of gas permeable materials although this area is being developed\cite{Femmer2014a}.
 Microfluidic cell culture devices are most commonly cast in PDMS as it is a convenient material for cell studies due to it's biocompatibility, optical properties, and gas permeability, facilitating oxygen control of cell environments\cite{Sia2003,Brennan2014}.
@@
 Oxygen control in cells studies is often overlooked by researchers, but important for mimicking conditions experienced by cells in vivo.
-Typically cell culture studies are preformed at 21\% oxygen, atmospheric oxygen conditions, although levels that cells experience in vivo are usually less\cite{Brennan2014}.
-For example tumors, in general, are hypoxic as they rapidly out grow their vasculature creating a hypoxic inner region\cite{Kumar2014}.
+Typically cell culture studies are preformed at 21\% oxygen, atmospheric oxygen conditions, although levels that cells experience in vivo are less than 21\% \cite{Brennan2014}.
+For example tumors are generally hypoxic as cancer cells rapidly out grow their vasculature creating a poorly perfused, hypoxic inner region\cite{Kumar2014}.
+Studying cancer cells under controlled hypoxic conditions is important in understanding the pathophysiology because research has shown hypoxia may enhance aggressive phenotypes, tumor progression, metastasis, ans resistance to therapy.
+Hypoxia is known to alter the transcription of many genes which are under the activity of the HIF (hypoxia inducible factor) family of transcriptional factors.
 To better study the role of oxygen levels in cancer gene expression a gas controlled culture system is required.
 
-Previously, we developed multiwell inserts for 6-well plates that controlled oxygen in a standard off-the self plate \cite{Oppegard2009, Oppegard2010}.
+Previously, we developed multiwell inserts for 6-well plates that controlled oxygen in a standard off-the shelf well plate \cite{Oppegard2009, Oppegard2010}.
 These devices were completely cast from PDMS and fabricated in a multiple bonding procedure.
@@
 Although available 3D printable materials are non-gas-permeable, the addition of a PDMS membrane following printing the passive microfluidic network is a simple addition allowing gas transfer. 
-In this case, having a gas-impermeable material for the bulk is advantageous as it reduces unwanted gas transfer. 
+In this case, having a gas-impermeable material for the bulk is advantageous as it reduces unwanted gas transfer from the bulk material prior to the gas exchange interface.
 The previous PDMS devices were Parylene coated along the convection channels to eliminate exchange of gas from the PDMS bulk, which again added to their complexity and is now longer needed.
@@
 
+CAD models were designed in Autodesk and Blender and printed via stereolithography in Watershed XC by Fineline Prototyping.
+The 3D part contained the microfluidic delivery channels, and was completed by adhering a gas permeable membrane of PDMS to enable diffusion of gas to the culture area using uncured PDMS as an adhesive.
+The PDMS membrane components are attached to the 3D-printed network with an additional, thin layer of PDMS that was applied as an adhesive to the membrane, secured in position on the end of each pillar, and allowed to cure in place.
+
 The device was designed to integrate with a multiwell format, specifically an off-the-shelf 24 well plate. 
-The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{Oppegard2010} and also incorporates an integrated distribution network and hose barbs to simplify device operation.
+The 24 well plate insert is designed to control gas in 4 rows of 6 wells each. 
+Each of the 4 rows can be controlled independently from an input and also incorporates an integrated distribution network and hose barbs to simplify device operation.
 The pillars extend into each well leaving a $\sim$500 $\mu$m gap for media between the diffusion membrane and the culture surface at the bottom of the well.
@@
 The device also features a pipe within a pipe design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Fig.~\ref{fig1}).
-Again the membranes are adhered with a thin layer of PDMS on the membrane and allowed to cure in place.
-
-The device was printed by Fineline Prototyping in Watershed XC using stereolithography.
-CAD models were designed and printed with microfluidic delivery channels, and then completed by adhering a gas permeable membrane of PDMS to enable diffusion of gas to the culture area using uncured PDMS as an adhesive.
 

### 2015-04-12 publishing/latex/paper.tex
fixed design/fabrication of methods

@@
 
-Printing is currently limited in choice of substate compatible with the 3D printing process.
+Printing is currently limited in choice of substrate compatible with the 3D printing process.
 Substrate options include many proprietary formulations which have been successfully used in a variety of applications.
@@
 \section*{Materials and Methods}
-\subsection*{Design of Insert}
-
-CAD models were designed in Autodesk and Blender and printed via stereolithography in Watershed XC by Fineline Prototyping.
-The 3D part contained the microfluidic delivery channels, and was completed by adhering a gas permeable membrane of PDMS to enable diffusion of gas to the culture area using uncured PDMS as an adhesive.
-The PDMS membrane components are attached to the 3D-printed network with an additional, thin layer of PDMS that was applied as an adhesive to the membrane, secured in position on the end of each pillar, and allowed to cure in place.
+\subsection*{Design of insert}
 
@@
 A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells (Fig.~\ref{fig1}).
-
 The device also features a pipe within a pipe design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Fig.~\ref{fig1}).
@@
 
+\subsection*{Fabrication of the insert}
+
+CAD models were designed in Autodesk and Blender and printed via stereolithography in Watershed XC by Fineline Prototyping.
+The 3D part contained the microfluidic delivery channels, and was completed by adhering a gas permeable membrane of PDMS to enable diffusion of gas to the culture area. 
+The PDMS membranes are fabricated by spin coating PDMS on a silicon wafer at 900 RPM to a thickness of $\sim$100 $\mu$m and curing at $70\,^{\circ}$ C.
+The PDMS membrane is cut to size and attached to the 3D-printed network with an additional, thin layer of PDMS that was applied as an adhesive to the membrane, secured in position on the end of each pillar, and allowed to cure in place.
+
 \subsection*{Oxygen characterization}
 
-Oxygen was measured with PtOEPK (Pt(II) Octaethylporphine ketone) planar sensors that were fixed to the bottom of a 24 well plate. 
+Oxygen was measured with PtOEPK (Pt(II) Octaethylporphine ketone) planar sensors that were fixed to the bottom of a 24-well plate. 
 The intensity of the sensor was measured and correlated to the concentration of oxygen with Stern-Volmer analysis (Fig.~\ref{fig2}).
-Gas was perfused through the device with negative pressure to reduce membrane debonding and was also found to reduce the number of bubbles formed in the culture chamber.
-The inlet tubing was placed in a cone with with a flow that exceed the vacuum flow rate so that the vacuum was always pulling in the gas of interest and not the room air.
+Gas was pulled through the device with negative pressure as a precaution to avoid bulging or detaching membranes, and bubble formation in the culture media.
+The outlet ports were connected to a water aspirator which pulled gas through the device from the inlet ports. 
+The inlet tubing was placed in an open cone that was flooded with gas from a tank with a flow that exceed the vacuum flow.
+ rate so that the vacuum was always pulling in the gas of interest and not the room air.
 All gas tanks used in the oxygen characterization were 5\% CO2 in addition to the desired gas mix in anticipation of cell culture experiments as CO2 can alter the fluorescence of the PtOEPK.

### 2015-04-13 publishing/latex/paper.tex
edited up to results

@@
 The intensity of the sensor was measured and correlated to the concentration of oxygen with Stern-Volmer analysis (Fig.~\ref{fig2}).
-Gas was pulled through the device with negative pressure as a precaution to avoid bulging or detaching membranes, and bubble formation in the culture media.
+Gas was pulled through the device with negative pressure as a precaution to avoid bulging or detaching membranes, as well as bubble formation in the culture media.
 The outlet ports were connected to a water aspirator which pulled gas through the device from the inlet ports.
-The inlet tubing was placed in an open cone that was flooded with gas from a tank with a flow that exceed the vacuum flow.
- rate so that the vacuum was always pulling in the gas of interest and not the room air.
-All gas tanks used in the oxygen characterization were 5\% CO2 in addition to the desired gas mix in anticipation of cell culture experiments as CO2 can alter the fluorescence of the PtOEPK.
-Intensity measurements were taken every five minutes for each well.
+The inlet tubing was placed in an open cone that was flooded with gas from a tank with a flow that exceed the vacuum flow so that the gas of interest is pulled into the inlet rather then room air.
+In this way, the pressure and therefore flow rate is equal across the 4 networks without having to balance flow from 4 pressurized sources, yet different gases of interest can be perfused via vacuum.
+
 Initially the inlets are fed with a 5\% \ce{CO2}, bal. air tank until the intensity stabilized.
@@
 Intensity measurements are then taken every five minutes for six hours.
-The this entire procedure was repeated three times for and N of three.
+All gas tanks used in the oxygen characterization were 5\% \ce{CO2} in addition to the desired gas mix in anticipation of cell culture experiments as \ce{CO2} can alter the fluorescence of the PtOEPK.
+The this entire procedure was repeated three times for and sample size of three.
 
@@
 
-\subsection*{Cell culture and hypoxia assay}
+\subsection*{Cell culture}
 
-Cancer cells were seeded in a 24 well plate.
+Human A549 cells were seeded at 30,000 cells per well in a 24-well plate.
+Cells were cultured in DMEM supplemented with 10\% FBS.
 When they reached $\sim$70\% confluency the 24-well insert is placed in the plate and the gases are perfused through the device in the same scheme as in the oxygen characterization.
-Each row of six wells experiences either 0, 5, 10 or 21\% \ce{O2}, with 5\% \ce{CO2} and balanced nitrogen.
-The assembly is placed in an incubator at $37\,^{\circ}\mathrm{C}$ for six hours (Fig.~\ref{fig3}).
+Each row of six wells experiences either 0\%, 5\%, 10\% or 21\% \ce{O2}, with 5\% \ce{CO2} and balanced nitrogen.
+The assembly is placed in an incubator at $37\,^{\circ}$C for six hours.
+
+\subsection*{Quantitative PCR}
+
+Following 6 h of oxygen modulation, the 24-well oxygen control insert was removed and culture media was aspirated.
+Cells in each well were washed twice with PBS, and 300 $/mu$L of a lysis solution consisting of 10 $\mu$L of $\beta$-mercaptoethanol (Sigma Aldrich) per 1 mL of lysis buffer (PureLink RNA Mini Kit; Invitrogen) was added to each well.
+The lysate from each well was collected as a sample.
+RNA was extracted according to the PureLink RNA Mini Kit manufacturer’s instructions.
+
+Synthesis of cDNA was performed using the High-Capacity cDNA Reverse Transcription Kit (Applied Biosystems), and quantitative PCR was carried out on ABI PRISM 700O (Applied Biosystems) in 25 $\mu$L reactions using Taqman Gene Expression Assays.
+Beta-2-microglobulin (B2M) served as the endogenous control for calculations of relative gene expression.
+
+\section*{Statistical analysis}
+
+Cell culture experiments were repeated three independent times.
+Data are expressed as the mean $\pm$ SD.
+One-way ANOVA with Tukey’s multiple comparison post-test performed by Prism 5 (Graphpad) determined significance.
+(Fig.~\ref{fig3}).
 

### 2015-04-13 publishing/latex/paper.tex
added citation for sensor fab

@@
 Oxygen was measured with PtOEPK (Pt(II) Octaethylporphine ketone) planar sensors that were fixed to the bottom of a 24-well plate.
-The intensity of the sensor was measured and correlated to the concentration of oxygen with Stern-Volmer analysis (Fig.~\ref{fig2}).
+Senors were prepared as discussed previously \cite{Sinkala2010}. 
+Briefly, polystyrene is dissolved in toluene to form a solution to which PtOEPK is mixed in before spinning coating to a thin layer and allowing the toluene to evaporate.
+The intensity of the sensor was measured with via florescence microscopy and correlated to the concentration of oxygen with Stern-Volmer analysis (Fig.~\ref{fig2}).
+
 Gas was pulled through the device with negative pressure as a precaution to avoid bulging or detaching membranes, as well as bubble formation in the culture media.
 The outlet ports were connected to a water aspirator which pulled gas through the device from the inlet ports.
-The inlet tubing was placed in an open cone that was flooded with gas from a tank with a flow that exceed the vacuum flow so that the gas of interest is pulled into the inlet rather then room air.
+The inlet tubing was placed in an open cone that was flooded with gas from a tank with a flow that exceed the vacuum flow so that the gas of interest is pulled into the inlet rather then room air due to the open connection.
 In this way, the pressure and therefore flow rate is equal across the 4 networks without having to balance flow from 4 pressurized sources, yet different gases of interest can be perfused via vacuum.
 
-Initially the inlets are fed with a 5\% \ce{CO2}, bal. air tank until the intensity stabilized.
+Initially the inlets are fed with a 5\% \ce{CO2}, balanced air tank until the intensity stabilized.
 The inlets are then switched to the control gas of either 0, 5 10 or 21\% \ce{O2}, each with 5\% \ce{CO2} and balanced with \ce{N2}.

### 2015-04-13 publishing/latex/paper.tex
added elly reference and minor edits

@@
 For example tumors are generally hypoxic as cancer cells rapidly out grow their vasculature creating a poorly perfused, hypoxic inner region\cite{Kumar2014}.
-Studying cancer cells under controlled hypoxic conditions is important in understanding the pathophysiology because research has shown hypoxia may enhance aggressive phenotypes, tumor progression, metastasis, ans resistance to therapy.
+Studying cancer cells under controlled hypoxic conditions is important in understanding the pathophysiology because research has shown hypoxia may enhance aggressive phenotypes, tumor progression, metastasis, and resistance to therapy.
 Hypoxia is known to alter the transcription of many genes which are under the activity of the HIF (hypoxia inducible factor) family of transcriptional factors.
@@
 All gas tanks used in the oxygen characterization were 5\% \ce{CO2} in addition to the desired gas mix in anticipation of cell culture experiments as \ce{CO2} can alter the fluorescence of the PtOEPK.
-The this entire procedure was repeated three times for and sample size of three.
+The this entire procedure was repeated three times for a sample size of three.
 
@@
 Following 6 h of oxygen modulation, the 24-well oxygen control insert was removed and culture media was aspirated.
-Cells in each well were washed twice with PBS, and 300 $/mu$L of a lysis solution consisting of 10 $\mu$L of $\beta$-mercaptoethanol (Sigma Aldrich) per 1 mL of lysis buffer (PureLink RNA Mini Kit; Invitrogen) was added to each well.
+Cells in each well were washed twice with PBS, and 300 $\mu$L of a lysis solution consisting of 10 $\mu$L of $\beta$-mercaptoethanol (Sigma Aldrich) per 1 mL of lysis buffer (PureLink RNA Mini Kit; Invitrogen) was added to each well.
 The lysate from each well was collected as a sample.
@@
 \caption{
-{\bf PCR Data.}  VEGF expression in A549 cells after exposure to different oxygen conditions.
+{\bf PCR Data.}  VEGF expression in A549 cells after exposure to different oxygen conditions set-up by the insert device. 
 }
@@
 Oxygen control in the 24-well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor placed at the bottom of the well, as shown in Fig.~\ref{fig2}.
-Oxygen was able to be controlled in each of the 6 wells equally from one gas input demonstrating the distribution network worked effectively.
 The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% \ce{O2} indefinitely, while 95\% \ce{N2}, 5\% \ce{CO2} is pumped through the device. 
 A different gas condition can be used in each separate iteration of the 6-well unit allowing 6 technical replicates of up to 4 different gas conditions in one 24 well plate (Fig.~\ref{fig2}).
+There was little variation in the oxygen levels measured in each of the 6 well controlled by a single inlet, demonstrating the distribution network worked effectively.
 
 \subsection*{Bioverifcation}
-The devices ability to control the gas environment is demonstrated with hypoxia influenced expression of mRNA in cancer cells (Fig.~\ref{fig3}).
-Oxygen levels of 21, 10, 5, and 0\% are applied to each set of 6 wells.
 
-More mRNA stuff for Megan to expand (Fig.~\ref{fig3}).
+Oxygen levels of 21\%, 10\%, 5\%, and 0\% were applied to each set of 6 wells in which A549 cells were cultured.
+Measurement of relative gene expression confirmed biological responsiveness of cells under the device’s control.
+The device’s ability to control the gas environment was demonstrated with hypoxia-induced upregulation of VEGFA mRNA in the A549 cells (Fig.~\ref{fig3}).
+Quantitative PCR showed a significant increase in the relative gene expression of VEGFA in wells exposed to 0\% \ce{O2} for 6 hours as compared to 21\% \ce{O2}.
+Hypoxia-induced alterations in gene expression usually indicate a HIF-transduced hypoxic signal in cells.
+When a HIF transcription factor undergoes nuclear translocation, it can initiate transcription of genes by binding to the hypoxia response element (HRE) on its target genes.
+VEGFA has previously been shown to have a functional HRE, and upregulation has been observed in A549 cells under hypoxic conditions.
 
 \subsection*{Discussion}
-This new iteration of the multi-well insert for oxygen control maintains the convenient features of the previous design.
+This new iteration of the multi-well insert for oxygen control maintains the convenient features of the previous design while improving distribution and interfacing with tubing due to the 3D-printed element.
 Oxygen control is preformed in an off-the-shelf culture plate allowing standard protocols to be used for analysis assays or imaging where additional protocols are often required when cells are seeded within microfluidic chips.
+The VEGFA gene expression in A549 cells confirms a biological response using the multi-well insert.
 
@@
 Moving forward with additive manufacturing of microfluidic devices is desirable as it will enable highly integrated designs without any additional fabrication.
-For this device an on-device gas mixer could allow more conditions in a single plate, perhaps even one per well or even gradients within wells while reducing the number of gas tanks required.
+For this device an in-device gas mixer could allow more conditions in a single plate, perhaps even one per well or even gradients within wells while reducing the number of gas tanks required as inputs.
 This design could also be applied to higher format plates such as 96-well plates.
@@
 3D printing microfluidic chips have been limited to non oxygen permeable materials. We demonstrate oxygen control in 3D printed devices the addition of a gas permeable PDMS membrane. 
-Oxygen control is demonstrated in a 24 well plate and PCR analysis of X in Y cells shows the device effectively controls oxygen as expected. 
+Oxygen control is demonstrated in a 24 well plate and PCR detection of upregulation of VEGFA mRNA in the A549 shows the device effectively controls oxygen as expected. 
 3D printing allows complex designs, integrated tubing connectors, and is comparable in price to standard PDMS fabrication. 

### 2015-04-13 publishing/latex/paper.tex
minor edits from DTE and title change

@@
 {\Large
-\textbf\newline{3D-Printed Microfluidic Oxygen Control Devices - Submission to PLOS ONE}
+\textbf\newline{3D-printed 24-well plate oxygen control device - Submission to PLOS ONE}
 }
@@
 \section*{Abstract}
-Recently 3D printing has emerged as a method for directly printing complete microfluidic chips, although printing materials have been limited to non-oxygen permeable materials.
+Recently 3D printing has emerged as a method for directly printing complete microfluidic devices, although printing materials have been limited to non-oxygen permeable materials.
 We demonstrate the addition of gas permeable PDMS (Polydimethylsiloxane) membranes to 3D printed microfluidic devices as a means to enable oxygen control cell culture studies.
-The incorporation of a 3D-printed device and gas-permeable membranes was demonstrated on an expanded 24-well version of our previous entirely PDMS device which was an insert for a 6-well plate.
+The incorporation of a 3D-printed device and gas-permeable membranes was demonstrated on a 24-well oxygen control device for standard multiwell plates.
 The direct printing allows integrated distribution channels and device geometries not possible with traditional planar lithography.
 With this device, four different oxygen conditions were able to be controlled and six wells were maintained under each oxygen condition. 
-We domonstrate enhanced transcrtiption of VEGFA (vascular endothelial growth factor A) gene with decreasing oxygen levels in human lung adenocarcinoma cells.
+We demonstrate enhanced transcription of VEGFA (vascular endothelial growth factor A) gene with decreasing oxygen levels in human lung adenocarcinoma cells.
 This is the first 3D-printed device that can be functionalized to control oxygen in cell culture.
@@
 New techniques for using a 3D-printed molds to produce devices\cite{Mcdonald2002,Gregory2013,King2014,Comina2014a} are also being developed, including fugitive ink methods\cite{Therriault2003,Miller2012,Bhargava2015}.
-To date, there are no widely available methods or materials to facilitate direct printing of gas permeable materials although this area is being developed\cite{Femmer2014a}.
+To date, there are no widely available methods or materials to facilitate direct printing of gas permeable materials although this area is actively being explored\cite{Femmer2014a}.
 Microfluidic cell culture devices are most commonly cast in PDMS as it is a convenient material for cell studies due to it's biocompatibility, optical properties, and gas permeability, facilitating oxygen control of cell environments\cite{Sia2003,Brennan2014}.
@@
 Oxygen control in cells studies is often overlooked by researchers, but important for mimicking conditions experienced by cells in vivo.
-Typically cell culture studies are preformed at 21\% oxygen, atmospheric oxygen conditions, although levels that cells experience in vivo are less than 21\% \cite{Brennan2014}.
-For example tumors are generally hypoxic as cancer cells rapidly out grow their vasculature creating a poorly perfused, hypoxic inner region\cite{Kumar2014}.
+Typically cell culture studies are performed at 21\% oxygen, atmospheric oxygen conditions, although levels that cells experience in vivo are less than 21\% \cite{Brennan2014}.
+For example tumors are generally hypoxic as cancer cells rapidly outgrow their vasculature creating a poorly perfused, hypoxic inner region\cite{Kumar2014}.
 Studying cancer cells under controlled hypoxic conditions is important in understanding the pathophysiology because research has shown hypoxia may enhance aggressive phenotypes, tumor progression, metastasis, and resistance to therapy.
@@
 Oxygen was measured with PtOEPK (Pt(II) Octaethylporphine ketone) planar sensors that were fixed to the bottom of a 24-well plate.
-Senors were prepared as discussed previously \cite{Sinkala2010}. 
+Sensors were prepared as discussed previously \cite{Sinkala2010}. 
 Briefly, polystyrene is dissolved in toluene to form a solution to which PtOEPK is mixed in before spinning coating to a thin layer and allowing the toluene to evaporate.
-The intensity of the sensor was measured with via florescence microscopy and correlated to the concentration of oxygen with Stern-Volmer analysis (Fig.~\ref{fig2}).
+The intensity of the sensor was measured with via fluorescence microscopy and correlated to the concentration of oxygen with Stern-Volmer analysis (Fig.~\ref{fig2}).
 
@@
 The outlet ports were connected to a water aspirator which pulled gas through the device from the inlet ports.
-The inlet tubing was placed in an open cone that was flooded with gas from a tank with a flow that exceed the vacuum flow so that the gas of interest is pulled into the inlet rather then room air due to the open connection.
+The inlet tubing was placed in an open cone that was flooded with gas from a tank with a flow that exceed the vacuum flow so that the gas of interest is pulled into the inlet rather than room air due to the open connection.
 In this way, the pressure and therefore flow rate is equal across the 4 networks without having to balance flow from 4 pressurized sources, yet different gases of interest can be perfused via vacuum.
@@
 This new iteration of the multi-well insert for oxygen control maintains the convenient features of the previous design while improving distribution and interfacing with tubing due to the 3D-printed element.
-Oxygen control is preformed in an off-the-shelf culture plate allowing standard protocols to be used for analysis assays or imaging where additional protocols are often required when cells are seeded within microfluidic chips.
+Oxygen control is performed in an off-the-shelf culture plate allowing standard protocols to be used for analysis assays or imaging where additional protocols are often required when cells are seeded within microfluidic chips.
 The VEGFA gene expression in A549 cells confirms a biological response using the multi-well insert.
@@
 While injection molding, hot embossing, or other industrial processes are cheaper when making hundreds to thousands of devices, it is not practical to make a injection mold when making tens to hundreds of devices.
-In addition, PDMS fabrication would be too time consuming, expensive, and the failure rate would be unacceptable. 3D printing is a perfect solution to these device fabrication needs.
+In addition, PDMS fabrication would be too time consuming, expensive, and the failure rate would be unacceptable. 3D printing is an excellent solution to these device fabrication needs.
 

### 2015-04-16 publishing/latex/paper.tex
minor edits
grammer edits and more citations

@@
 {\Large
-\textbf\newline{3D-printed 24-well plate oxygen control device - Submission to PLOS ONE}
+\textbf\newline{3D-Printed 24-Well Plate Oxygen Control Device - Submission to PLOS ONE}
 }
@@
 \section*{Abstract}
-Recently 3D printing has emerged as a method for directly printing complete microfluidic devices, although printing materials have been limited to non-oxygen permeable materials.
-We demonstrate the addition of gas permeable PDMS (Polydimethylsiloxane) membranes to 3D printed microfluidic devices as a means to enable oxygen control cell culture studies.
+Recently 3D printing has emerged as a method for directly printing complete microfluidic devices, although printing materials have been limited to oxygen-impermeable materials.
+We demonstrate the addition of gas permeable PDMS (Polydimethylsiloxane) membranes to 3D-printed microfluidic devices as a means to enable oxygen control cell culture studies.
 The incorporation of a 3D-printed device and gas-permeable membranes was demonstrated on a 24-well oxygen control device for standard multiwell plates.
 The direct printing allows integrated distribution channels and device geometries not possible with traditional planar lithography.
-With this device, four different oxygen conditions were able to be controlled and six wells were maintained under each oxygen condition. 
-We demonstrate enhanced transcription of VEGFA (vascular endothelial growth factor A) gene with decreasing oxygen levels in human lung adenocarcinoma cells.
+With this device, four different oxygen conditions were able to be controlled, and six wells were maintained under each oxygen condition. 
+We demonstrate enhanced transcription of the gene VEGFA (vascular endothelial growth factor A) with decreasing oxygen levels in human lung adenocarcinoma cells.
 This is the first 3D-printed device that can be functionalized to control oxygen in cell culture.
@@
 \section*{Introduction}
-Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
+Here we report on the development of 3D-printed microfluidic devices for the control of oxygen in cell culture microenvironments.
 We demonstrate a device that nests into a 24-well culture plate to control gas in each row of the plate independently of the incubator's condition.
@@
 3D printed devices have been used for neuroengineering applications\cite{Tek2008}, inexpensive and high-throughput reactionware,\cite{Kitson2012,Symes2012, Kitson2014}, culturing and imaging arrays of seedlings\cite{Busch2012}, measuring dopamine and ATP levels in biological samples with an integrated electrode\cite{Erkal2014}, or plate reader\cite{Chen2014}, and a bacteria separation flow assay\cite{Lee2014a,Lee2015}.
-Other 3D printed fluidic devices include pneumatic valves\cite{Au2015} a custom NMR cell\cite{Causier2015}, a rapid reconstitution package for lyophilized drugs\cite{Chi2014} and flow plates for a water electrolysis system\cite{Chisholm2014}.
+Other 3D-printed fluidic devices include pneumatic valves\cite{Au2015} a custom NMR cell\cite{Causier2015}, a rapid reconstitution package for lyophilized drugs\cite{Chi2014} and flow plates for a water electrolysis system\cite{Chisholm2014}.
 
@@
 Substrate options include many proprietary formulations which have been successfully used in a variety of applications.
-New techniques for using a 3D-printed molds to produce devices\cite{Mcdonald2002,Gregory2013,King2014,Comina2014a} are also being developed, including fugitive ink methods\cite{Therriault2003,Miller2012,Bhargava2015}.
-To date, there are no widely available methods or materials to facilitate direct printing of gas permeable materials although this area is actively being explored\cite{Femmer2014a}.
-Microfluidic cell culture devices are most commonly cast in PDMS as it is a convenient material for cell studies due to it's biocompatibility, optical properties, and gas permeability, facilitating oxygen control of cell environments\cite{Sia2003,Brennan2014}.
+New techniques for using 3D-printed molds to produce devices\cite{Mcdonald2002,Gregory2013,King2014,Comina2014a,Kamei2015} are also being developed, including fugitive ink methods\cite{Therriault2003,Miller2012,Bhargava2015}.
+To date, there are no widely available methods or materials to facilitate direct printing of gas-permeable materials, although this area is actively being explored\cite{Femmer2014a}.
+Microfluidic cell culture devices are most commonly cast in PDMS as it is a convenient material for cell studies due to its biocompatibility, optical properties, and gas permeability, facilitating oxygen control of cell environments\cite{Sia2003,Brennan2014}.
 
@@
 Typically cell culture studies are performed at 21\% oxygen, atmospheric oxygen conditions, although levels that cells experience in vivo are less than 21\% \cite{Brennan2014}.
-For example tumors are generally hypoxic as cancer cells rapidly outgrow their vasculature creating a poorly perfused, hypoxic inner region\cite{Kumar2014}.
-Studying cancer cells under controlled hypoxic conditions is important in understanding the pathophysiology because research has shown hypoxia may enhance aggressive phenotypes, tumor progression, metastasis, and resistance to therapy.
-Hypoxia is known to alter the transcription of many genes which are under the activity of the HIF (hypoxia inducible factor) family of transcriptional factors.
-To better study the role of oxygen levels in cancer gene expression a gas controlled culture system is required.
+For example, tumors are generally hypoxic as cancer cells rapidly outgrow their vasculature creating a poorly perfused, hypoxic inner region\cite{Kumar2014}.
+Studying cancer cells under controlled hypoxic conditions is important in understanding the pathophysiology because research has shown hypoxia may enhance aggressive phenotypes, tumor progression, metastasis, and resistance to therapy\cite{Vaupel2004,Vaupel2007,Gilkes2014}.
+Hypoxia is known to alter the transcription of many genes which are under the activity of the HIF (hypoxia inducible factor) family of transcriptional factors\cite{Ke2006,Semenza1999,Semenza2002}.
+To better study the role of oxygen levels in cancer gene expression, a gas controlled culture system is required.
 
@@
 Utilizing 3D printing for the fabrication allowed further features to be incorporated such as integrated distribution channels to eliminate the connection tubings between wells and hose barbs for better tubing connections, while eliminating fabrication time and failure rate.
-Although available 3D printable materials are non-gas-permeable, the addition of a PDMS membrane following printing the passive microfluidic network is a simple addition allowing gas transfer. 
+Although available 3D printable materials are gas-impermeable, the addition of a PDMS membrane following printing of the passive microfluidic network is a simple addition allowing gas transfer. 
 In this case, having a gas-impermeable material for the bulk is advantageous as it reduces unwanted gas transfer from the bulk material prior to the gas exchange interface.
-The previous PDMS devices were Parylene coated along the convection channels to eliminate exchange of gas from the PDMS bulk, which again added to their complexity and is now longer needed.
-Convection and distribution of the gas is done in the impermeable material eliminating dilution of the gas before reaching the diffusion layer.
+The previous PDMS devices were Parylene coated along the convection channels to eliminate exchange of gas from the PDMS bulk, which again added to their complexity and is no longer needed.
+Convection and distribution of the gas is done in the impermeable material, eliminating dilution of the gas before reaching the diffusion layer.
 
@@
 
-The device was designed to integrate with a multiwell format, specifically an off-the-shelf 24 well plate. 
-The 24 well plate insert is designed to control gas in 4 rows of 6 wells each. 
+The device was designed to integrate with a multiwell format, specifically an off-the-shelf 24-well plate. 
+The 24-well plate insert was designed to control gas in 4 rows of 6 wells each. 
 Each of the 4 rows can be controlled independently from an input and also incorporates an integrated distribution network and hose barbs to simplify device operation.
@@
 (A) Rendering of whole 3D printed part.
-An inlet and outlet barb allows perfusion of gas to control 6 channels.
+An inlet and outlet barb allows perfusion of gas to control 6 wells.
 (B) At the bottom of each pillar gas entering from the outer channel flows along the PDMS membrane (blue), which is supported by micropillars, and exhausts via the inner pipe.
@@
 The arrows indicate the flow direction.
-The incoming gas enters enters the outer pipe on its way to the bottom of the well and returns through the inner pipe.
+The incoming gas enters the outer pipe on its way to the bottom of the well and returns through the inner pipe.
 (D) Photo of the device with dyed channels in a 24-well plate.
@@
 CAD models were designed in Autodesk and Blender and printed via stereolithography in Watershed XC by Fineline Prototyping.
-The 3D part contained the microfluidic delivery channels, and was completed by adhering a gas permeable membrane of PDMS to enable diffusion of gas to the culture area. 
-The PDMS membranes are fabricated by spin coating PDMS on a silicon wafer at 900 RPM to a thickness of $\sim$100 $\mu$m and curing at $70\,^{\circ}$ C.
-The PDMS membrane is cut to size and attached to the 3D-printed network with an additional, thin layer of PDMS that was applied as an adhesive to the membrane, secured in position on the end of each pillar, and allowed to cure in place.
+The 3D part contained the microfluidic delivery channels, and was completed by adhering a gas-permeable membrane of PDMS to enable diffusion of gas to the culture area. 
+The PDMS membranes were fabricated by spin coating PDMS on a silicon wafer at 900 RPM to a thickness of $\sim$100 $\mu$m and curing at $70\,^{\circ}$C for 30 minutes.
+The PDMS membrane was cut to size and attached to the 3D-printed network with an additional, thin layer of PDMS that was applied as an adhesive to the membrane, secured in position on the end of each pillar, and allowed to cure in place.
 
@@
 Oxygen was measured with PtOEPK (Pt(II) Octaethylporphine ketone) planar sensors that were fixed to the bottom of a 24-well plate.
-Sensors were prepared as discussed previously \cite{Sinkala2010}. 
-Briefly, polystyrene is dissolved in toluene to form a solution to which PtOEPK is mixed in before spinning coating to a thin layer and allowing the toluene to evaporate.
-The intensity of the sensor was measured with via fluorescence microscopy and correlated to the concentration of oxygen with Stern-Volmer analysis (Fig.~\ref{fig2}).
+Sensors were prepared as discussed previously \cite{Sinkala2010,Rexius-Hall2014}. 
+Briefly, polystyrene was dissolved in toluene to form a solution to which PtOEPK was mixed in before spin coating to a thin layer and allowing the toluene to evaporate.
+The intensity of the sensor was measured with via fluorescence microscopy and correlated to the concentration of oxygen with Stern-Volmer analysis.
 
@@
 The outlet ports were connected to a water aspirator which pulled gas through the device from the inlet ports.
-The inlet tubing was placed in an open cone that was flooded with gas from a tank with a flow that exceed the vacuum flow so that the gas of interest is pulled into the inlet rather than room air due to the open connection.
-In this way, the pressure and therefore flow rate is equal across the 4 networks without having to balance flow from 4 pressurized sources, yet different gases of interest can be perfused via vacuum.
+The inlet tubing was placed in an open cone that was flooded with gas from a tank with a flow that exceed the vacuum flow so that the gas of interest was pulled into the inlet rather than room air due to the open connection.
+In this way, the pressure, and therefore flow rate, was equal across the 4 networks without having to balance flow from 4 pressurized sources, yet different gases of interest can be perfused via vacuum.
 
 Initially the inlets are fed with a 5\% \ce{CO2}, balanced air tank until the intensity stabilized.
-The inlets are then switched to the control gas of either 0, 5 10 or 21\% \ce{O2}, each with 5\% \ce{CO2} and balanced with \ce{N2}.
-Intensity measurements are then taken every five minutes for six hours.
-All gas tanks used in the oxygen characterization were 5\% \ce{CO2} in addition to the desired gas mix in anticipation of cell culture experiments as \ce{CO2} can alter the fluorescence of the PtOEPK.
-The this entire procedure was repeated three times for a sample size of three.
-
-\begin{figure}[h]
-\caption{
-{\bf Oxygen Characterization.} 
-(A) Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device.
-Error bars are the standard deviation N=3.
-(B) Four oxygen conditions are demonstrated in a 24-well plate.
-Each 6-well row of the plate can be controlled independently.  
-Mean N=3 error bars not included.
-}
-\label{fig2}
-\end{figure}
+The inlets were then switched to the control gas of either 0, 5, 10, or 21\% \ce{O2}, each with 5\% \ce{CO2} and balanced with \ce{N2}.
+Intensity measurements were then taken every five minutes for six hours.
+All gas tanks used in the oxygen characterization were 5\% \ce{CO2}  in addition to the desired gas mix in anticipation of cell culture experiments (where \ce{CO2} is necessary to buffer the culture media) as \ce{CO2} can alter the fluorescence of the PtOEPK.
+The this entire procedure was repeated three independent times.
 
@@
 
-Human A549 cells were seeded at 30,000 cells per well in a 24-well plate.
+Human lung adenocarcinoma (A549) cells were seeded at 30,000 cells per well in a 24-well plate.
 Cells were cultured in DMEM supplemented with 10\% FBS.
-When they reached $\sim$70\% confluency the 24-well insert is placed in the plate and the gases are perfused through the device in the same scheme as in the oxygen characterization.
-Each row of six wells experiences either 0\%, 5\%, 10\% or 21\% \ce{O2}, with 5\% \ce{CO2} and balanced nitrogen.
-The assembly is placed in an incubator at $37\,^{\circ}$C for six hours.
+After reaching $\sim$70\% confluency, the 24-well insert was placed in the plate and the gases were perfused through the device in the same scheme as in the oxygen characterization.
+Each row of six wells experienced either 0\%, 5\%, 10\% or 21\% \ce{O2}, with 5\% \ce{CO2} and balanced nitrogen.
+The assembly was placed in an incubator at $37\,^{\circ}$C for six hours.
 
@@
 
-Following 6 h of oxygen modulation, the 24-well oxygen control insert was removed and culture media was aspirated.
+Following six hours of oxygen modulation, the 24-well oxygen control insert was removed and culture media was aspirated.
 Cells in each well were washed twice with PBS, and 300 $\mu$L of a lysis solution consisting of 10 $\mu$L of $\beta$-mercaptoethanol (Sigma Aldrich) per 1 mL of lysis buffer (PureLink RNA Mini Kit; Invitrogen) was added to each well.
@@
 Beta-2-microglobulin (B2M) served as the endogenous control for calculations of relative gene expression.
+Six technical replicates from the 6-well control unit were processed for each of four oxygen conditions (0\%, 5\%, 10\% and 21\% \ce{O2}) in three independent experiments.
 
-\section*{Statistical analysis}
+\subsection*{Statistical analysis}
 
@@
 One-way ANOVA with Tukey’s multiple comparison post-test performed by Prism 5 (Graphpad) determined significance.
-(Fig.~\ref{fig3}).
-
-\begin{figure}[h]
-\caption{
-{\bf PCR Data.}  VEGF expression in A549 cells after exposure to different oxygen conditions set-up by the insert device. 
-}
-\label{fig3}
-\end{figure}
 
@@
 \subsection*{Oxygen Control}
-Oxygen control in the 24-well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor placed at the bottom of the well, as shown in Fig.~\ref{fig2}.
+Oxygen control in the 24-well insert device was quantified with a platinum-based (PtOEPK) planar oxygen sensor placed at the bottom of the well, as shown in Fig.~\ref{fig2}.
 The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% \ce{O2} indefinitely, while 95\% \ce{N2}, 5\% \ce{CO2} is pumped through the device. 
-A different gas condition can be used in each separate iteration of the 6-well unit allowing 6 technical replicates of up to 4 different gas conditions in one 24 well plate (Fig.~\ref{fig2}).
-There was little variation in the oxygen levels measured in each of the 6 well controlled by a single inlet, demonstrating the distribution network worked effectively.
+A different gas condition can be used in each separate iteration of the 6-well unit allowing 6 technical replicates of up to 4 different gas conditions in one 24-well plate (Fig.~\ref{fig2}).
+There was little variation in the oxygen levels measured in each of the 6 wells controlled by a single inlet, demonstrating the distribution network worked effectively.
+
+\begin{figure}[h]
+\caption{
+{\bf Oxygen Characterization.} 
+(A) Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device.
+Error bars are the standard deviation N=3.
+(B) Four oxygen conditions are demonstrated in a 24-well plate.
+Each 6-well row of the plate can be controlled independently.  
+Mean N=3 error bars not included.
+}
+\label{fig2}
+\end{figure}
 
@@
 Hypoxia-induced alterations in gene expression usually indicate a HIF-transduced hypoxic signal in cells.
-When a HIF transcription factor undergoes nuclear translocation, it can initiate transcription of genes by binding to the hypoxia response element (HRE) on its target genes.
-VEGFA has previously been shown to have a functional HRE, and upregulation has been observed in A549 cells under hypoxic conditions.
+When a HIF transcription factor undergoes nuclear translocation, it can initiate transcription of genes by binding to the hypoxia response element (HRE)\cite{Lee2004} on its target genes.
+VEGFA has previously been shown to have a functional HRE, and upregulation has been observed in A549 cells under hypoxic conditions\cite{RohrerBley2011}.
+
+\begin{figure}[h]
+\caption{
+{\bf PCR Data.}  VEGFA expression in A549 cells after exposure to different oxygen conditions set-up by the insert device. Data are expressed as mean $\pm$ SD, N=3.
+}
+\label{fig3}
+\end{figure}
 
@@
 In PDMS devices the layers are bonded permanently via plasma bonding so damage to a membrane is not repairable.
-3D-printing also enables higher levels of intricacy without any additional fabrication allowing us to include the distribution network and the 'pipe within a pipe' design. 
+3D-printing also enables higher levels of intricacy without any additional fabrication, allowing us to include the distribution network, overlapping of channels in the z-axis, and the 'pipe within a pipe' design.
 A comparable PDMS device would require several additional microfabricated layers to be manually aligned to reproduce just the distribution network.
@@
 \section*{Conclusion}
-3D printing microfluidic chips have been limited to non oxygen permeable materials. We demonstrate oxygen control in 3D printed devices the addition of a gas permeable PDMS membrane. 
-Oxygen control is demonstrated in a 24 well plate and PCR detection of upregulation of VEGFA mRNA in the A549 shows the device effectively controls oxygen as expected. 
+3D printing microfluidic chips have been limited to oxygen-impermeable materials.
+We demonstrate oxygen control in 3D-printed devices with the addition of a gas permeable PDMS membrane. 
+Oxygen control is demonstrated in a 24-well plate and PCR detection of upregulation of VEGFA mRNA in A549 cells shows the device effectively controls oxygen as expected. 
 3D printing allows complex designs, integrated tubing connectors, and is comparable in price to standard PDMS fabrication. 
 This technique represents a bridge to commercialization where robust devices can be more easily shared and disseminated. 
-While injection molding, hot embossing, or other industrial processes are cheaper when making hundreds to thousands of devices, it is not practical to make a injection mold when making tens to hundreds of devices.
+While injection molding, hot embossing, or other industrial processes are cheaper when making hundreds to thousands of devices, it is not practical to make an injection mold when making tens to hundreds of devices.
 In addition, PDMS fabrication would be too time consuming, expensive, and the failure rate would be unacceptable. 3D printing is an excellent solution to these device fabrication needs.

### 2015-04-17 publishing/latex/paper.tex
updated figure 2 and captions, final edits to manuscirpt

@@
 Many prototypical microfluidic device features have been recreated with 3D printing as a proof of concept for this new fabrication technique \cite{ Au2014, Shallan2014} including modular re-configurable units\cite{Yuen2008,Bhargava2014,Lee2014}.
-3D printed devices have been used for neuroengineering applications\cite{Tek2008}, inexpensive and high-throughput reactionware,\cite{Kitson2012,Symes2012, Kitson2014}, culturing and imaging arrays of seedlings\cite{Busch2012}, measuring dopamine and ATP levels in biological samples with an integrated electrode\cite{Erkal2014}, or plate reader\cite{Chen2014}, and a bacteria separation flow assay\cite{Lee2014a,Lee2015}.
+3D printed devices have been used for neuroengineering applications\cite{Tek2008}, inexpensive and high-throughput reactionware,\cite{Kitson2012,Symes2012,Kitson2013,Kitson2014}, culturing and imaging arrays of seedlings\cite{Busch2012}, measuring dopamine and ATP levels in biological samples with an integrated electrode\cite{Erkal2014}, or plate reader\cite{Chen2014}, and a bacteria separation flow assay\cite{Lee2014a,Lee2015}.
 Other 3D-printed fluidic devices include pneumatic valves\cite{Au2015} a custom NMR cell\cite{Causier2015}, a rapid reconstitution package for lyophilized drugs\cite{Chi2014} and flow plates for a water electrolysis system\cite{Chisholm2014}.
@@
 \section*{Results}
-\subsection*{Oxygen Control}
+\subsection*{Oxygen control}
 Oxygen control in the 24-well insert device was quantified with a platinum-based (PtOEPK) planar oxygen sensor placed at the bottom of the well, as shown in Fig.~\ref{fig2}.
